---
title: "UN_assembly_proj"
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    
---

```{r setup, include=FALSE}
# ignore the errors
knitr::opts_chunk$set(error = TRUE)
```


# Dataset

```{r}
assembly <- readr::read_csv("2024_09_12_ga_resolutions_voting.csv")
head(assembly)
```

```{r}
unique(assembly['ms_name'])
```

Country name descrepancies: Yogoslavia republik, USSR, Ukranian SSR, Belorussian SSR, Turkey and Turkiye, East and West Germany, Former Yugoslav Republic of Macedonia, Serbia and Montenegro, etc.


```{r}
str(assembly)
```

For now, working on the year 2020. Might change after the research
```{r}
# keeping year 2020
assembly2020 <- assembly |>
  filter(lubridate::year(date) == 2020)
```

```{r}
unique(assembly2020['agenda_title'])
```

```{r}
unique(filter(assembly2020, agenda_title == 'The situation in the Middle East.'))
#about Syria
```


Subsetting by the topic:
```{r}
count(filter(assembly2020, subjects == 'PALESTINE QUESTION')) 
assembly2020_pal <- assembly2020 |> 
  filter(subjects == 'PALESTINE QUESTION')

```

Getting unique assembly titles of Palestine topic
```{r}
unique(assembly2020_pal['title'])
```


Filtering the dataset:
```{r}
assembly2020_pal <- assembly2020_pal[c('ms_name', 'ms_vote', 'resolution', 
                                       'title')]
```


```{r}
# keeping rows where the vote is 'Yes'
yes_votes2020_pal <- assembly2020_pal |> 
  filter(ms_vote == "Y")
```

```{r}
unique(yes_votes2020_pal['ms_name'])
#149 countries voted yes at least once out of four assemblies
```


# Making network

```{r}
library(tidyverse)

# making edges
edges <- yes_votes2020_pal |>
  group_by(resolution) |>
  summarise(pairs = list(combn(ms_name, 2, simplify = FALSE))) |>
  unnest(pairs) |>
  mutate(country1 = map_chr(pairs, 1),
         country2 = map_chr(pairs, 2)) |>
  select(country1, country2)
```


```{r}
# making weights
weighted_edges <- edges %>%
  group_by(country1, country2) %>%
  summarise(weight = n(), .groups = 'drop')
```

`weight` here represents how many times a country voted yes together.

```{r}
# threshold because network is fully connected
weighted_edges <- weighted_edges %>%
  filter(weight >= 2) #include only edges where weight is 2 or more
```


```{r}
# creating networks
assembly_graph <- igraph::graph_from_data_frame(weighted_edges, directed = FALSE)

# Add edge weights to the graph
igraph::E(assembly_graph)$weight <- weighted_edges$weight
```


```{r}
print(assembly_graph)
```
149 nodes (same as N0 unique countries). 10900 edges (142, 9899 after threshold)

```{r}
igraph::vertex_attr_names(assembly_graph)
igraph::edge_attr_names(assembly_graph)
```


```{r}
plot(assembly_graph, vertex.size = 10, 
     vertex.label.cex = 0.5,
     vertex.color = 'gray80',
     edge.color = igraph::E(assembly_graph)$weight)
```



```{r}
igraph::is.connected(assembly_graph)
```
The network is fully connected


```{r}
igraph::edge_density(assembly_graph)
```
Density is very big





```{r}
assembly_n <- snafun::to_network(assembly_graph)
assembly_n
```

## Voting 'No' together

```{r}
# keeping rows where the vote is 'No'
no_votes2020_pal <- assembly2020_pal |> 
  filter(ms_vote == "N")
```


```{r}
# making edges
edges_n <- no_votes2020_pal |>
  group_by(resolution) |>
  summarise(pairs = list(combn(ms_name, 2, simplify = FALSE))) |>
  unnest(pairs) |>
  mutate(country1 = map_chr(pairs, 1),
         country2 = map_chr(pairs, 2)) |>
  select(country1, country2)

# making weights
weighted_edges_n <- edges_n %>%
  group_by(country1, country2) %>%
  summarise(weight = n(), .groups = 'drop')
```


```{r}
# creating networks
assembly_NO <- igraph::graph_from_data_frame(weighted_edges_n, directed = FALSE)

# Add edge weights to the graph
igraph::E(assembly_NO)$weight <- weighted_edges_n$weight
```


```{r}
print(assembly_NO)
```

```{r}
plot(assembly_NO, vertex.size = 10, 
     vertex.label.cex = 0.5,
     vertex.color = 'gray80',
     edge.color = igraph::E(assembly_NO)$weight)
```
The 'No' graph looks a bit better.

## Years 2020 and 2021


GERGM: we can use weights and predict a continuous number (countries that voted together 4 times).





