---
title: "UN_assembly_proj"
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    
---

```{r setup, include=FALSE}
# ignore the errors
knitr::opts_chunk$set(error = TRUE)

library(dplyr)
```


# Dataset

```{r}
assembly <- readr::read_csv("2024_09_12_ga_resolutions_voting.csv")
head(assembly)
```

```{r}
unique(assembly['ms_name'])
```

Country name descrepancies: Yogoslavia republik, USSR, Ukranian SSR, Belorussian SSR, Turkey and Turkiye, East and West Germany, Former Yugoslav Republic of Macedonia, Serbia and Montenegro, etc.


```{r}
str(assembly)
```

For now, working on the year 2020. Might change after the research
```{r}
# keeping year 2020
assembly2020 <- assembly %>%
  filter(lubridate::year(date) == 2020)
```


```{r}
unique(assembly2020['agenda_title'])
```

```{r}
unique(filter(assembly2020, agenda_title == 'The situation in the Middle East.'))
#about Syria
```


Subsetting by the topic:
```{r}
count(filter(assembly2020, subjects == 'PALESTINE QUESTION')) 
assembly2020_pal <- assembly2020 |> 
  filter(subjects == 'PALESTINE QUESTION')

```

Getting unique assembly titles of Palestine topic
```{r}
unique(assembly2020_pal['title'])
```


Filtering the dataset:
```{r}
assembly2020_pal <- assembly2020_pal[c('ms_name', 'ms_vote', 'resolution', 
                                       'title')]
```


```{r}
# keeping rows where the vote is 'Yes'
yes_votes2020_pal <- assembly2020_pal |> 
  filter(ms_vote == "Y")
```

```{r}
unique(yes_votes2020_pal['ms_name'])
#149 countries voted yes at least once out of four assemblies
```


# Making network

```{r}
library(tidyverse)

# making edges
edges <- yes_votes2020_pal |>
  group_by(resolution) |>
  summarise(pairs = list(combn(ms_name, 2, simplify = FALSE))) |>
  unnest(pairs) |>
  mutate(country1 = map_chr(pairs, 1),
         country2 = map_chr(pairs, 2)) |>
  select(country1, country2)
```


```{r}
# making weights
weighted_edges <- edges %>%
  group_by(country1, country2) %>%
  summarise(weight = n(), .groups = 'drop')
```

`weight` here represents how many times a country voted yes together.

```{r}
# threshold because network is fully connected
weighted_edges <- weighted_edges %>%
  filter(weight >= 2) #include only edges where weight is 2 or more
```


```{r}
# creating networks
assembly_graph <- igraph::graph_from_data_frame(weighted_edges, directed = FALSE)

# Add edge weights to the graph
igraph::E(assembly_graph)$weight <- weighted_edges$weight
```


```{r}
print(assembly_graph)
```
149 nodes (same as N0 unique countries). 10900 edges (142, 9899 after threshold)

```{r}
igraph::vertex_attr_names(assembly_graph)
igraph::edge_attr_names(assembly_graph)
```


```{r}
plot(assembly_graph, vertex.size = 10, 
     vertex.label.cex = 0.5,
     vertex.color = 'gray80',
     edge.color = igraph::E(assembly_graph)$weight)
```



```{r}
igraph::is.connected(assembly_graph)
```
The network is fully connected


```{r}
igraph::edge_density(assembly_graph)
```
Density is very big





```{r}
assembly_n <- snafun::to_network(assembly_graph)
assembly_n
```

## Voting 'No' together

```{r}
# keeping rows where the vote is 'No'
no_votes2020_pal <- assembly2020_pal |> 
  filter(ms_vote == "N")
```


```{r}
# making edges
edges_n <- no_votes2020_pal |>
  group_by(resolution) |>
  summarise(pairs = list(combn(ms_name, 2, simplify = FALSE))) |>
  unnest(pairs) |>
  mutate(country1 = map_chr(pairs, 1),
         country2 = map_chr(pairs, 2)) |>
  select(country1, country2)

# making weights
weighted_edges_n <- edges_n %>%
  group_by(country1, country2) %>%
  summarise(weight = n(), .groups = 'drop')
```


```{r}
# creating networks
assembly_NO <- igraph::graph_from_data_frame(weighted_edges_n, directed = FALSE)

# Add edge weights to the graph
igraph::E(assembly_NO)$weight <- weighted_edges_n$weight
```


```{r}
print(assembly_NO)
```

```{r}
plot(assembly_NO, vertex.size = 10, 
     vertex.label.cex = 0.5,
     vertex.color = 'gray80',
     edge.color = igraph::E(assembly_NO)$weight)
```
The 'No' graph looks a bit better.

## Years 2020 and 2021


GERGM: we can use weights and predict a continuous number (countries that voted together 4 times).


## Same method as B. Kim et al


```{r}
library(dplyr)

assembly <- assembly |> dplyr::mutate(date = lubridate::ymd(date))

data <- assembly %>% 
  dplyr::mutate(year = lubridate::year(date)) %>% 
  filter(year %in% c(2020, 2021, 2022, 2023))
```


```{r}
unique(data['ms_name'])
```


```{r}
#TÜRKİYE case
data <- data %>%
  mutate(country = stringr::str_replace(ms_name, "TURKEY", "TÜRKİYE"))
```


```{r}
# NETHERLANDS (KINGDOM OF THE) case
data %>%
  filter(ms_name == c("NETHERLANDS (KINGDOM OF THE)", "NETHERLANDS"))
```
We will treat NETHERLANDS (KINGDOM OF THE) and NETHERLANDS as two separate countries.


```{r}
unique(data['subjects'])
```

**Related topics**: PALESTINE QUESTION, TERRITORIES OCCUPIED BY ISRAEL--SETTLEMENT POLICY, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS--REPORTS, TERRITORIES OCCUPIED BY ISRAEL--NATURAL RESOURCES, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS

```{r}
# include subject where words PALESTINE and ISRAEL are present
data <- data |> 
  filter(stringr::str_detect(subjects, "PALESTINE|ISRAEL"))
```


```{r}
data <- data[c('ms_code', 'ms_vote', 'resolution', 
                                       'title')]
# deleting NV votes
data <- data |> 
  filter(ms_vote != "NV")
```


```{r}
# creating pairwise agreements
agreement_scores <- data %>%
  group_by(resolution) %>%
  summarise(pairs = list(combn(ms_code, 2, simplify = FALSE)),
            votes = list(combn(ms_vote, 2, simplify = FALSE))) %>%
  tidyr::unnest(cols = c(pairs, votes)) %>%
  mutate(country1 = purrr::map_chr(pairs, 1),
         country2 = purrr::map_chr(pairs, 2),
         vote1 = purrr::map_chr(votes, 1),
         vote2 = purrr::map_chr(votes, 2),
         agreement = case_when(
           vote1 == vote2 ~ 1,                    # Exact match (Y/Y, N/N, A/A)
           (vote1 == "Y" & vote2 == "A") | 
           (vote1 == "A" & vote2 == "Y") |
           (vote1 == "N" & vote2 == "A") | 
           (vote1 == "A" & vote2 == "N") ~ 0.5,         # Partial match (Y/A, N/A)
           TRUE ~ 0                                    # No agreement
         )) %>%
  select(country1, country2, resolution, agreement)
```


```{r}
weighted_edges <- agreement_scores %>%
  group_by(country1, country2) %>%
  summarise(weight = sum(agreement), .groups = 'drop')
```


```{r}
min(weighted_edges$weight)
max(weighted_edges$weight)
```



```{r}
# create a network
UNGA_graph <- igraph::graph_from_data_frame(weighted_edges, directed = FALSE)

#add weights to edge attributes
igraph::E(UNGA_graph)$weight <- weighted_edges$weight
```


```{r}
print(UNGA_graph)
```

The edge is this network is the level of agreement on votes. Weight - sum of agreement scores.


```{r}
plot(UNGA_graph, 
     edge.width = igraph::E(UNGA_graph)$weight, 
     vertex.size = 5, 
     vertex.label.cex = 0.7)
```

```{r}
igraph::is_connected(UNGA_graph)
igraph::edge_density(UNGA_graph)
igraph::degree_distribution(UNGA_graph)
```



Selecting a threshold that reduces the density of your network to a desired level:
```{r}
#target_density <- 0.1

#while (igraph::edge_density(UNGA_graph) > target_density) {
  # Remove weakest edges 
#  weakest_edge <- igraph::E(UNGA_graph)[which.min(igraph::E(UNGA_graph)$weight)]
#  UNGA_graph <- igraph::delete_edges(UNGA_graph, weakest_edge)
#}
```


# GERGM

```{r}
class(weighted_edges)
```

Transforming this dataframe into adjacency matrix
```{r}
all_countries <- unique(c(weighted_edges$country1, weighted_edges$country2))

adj_matrix_df <- weighted_edges %>%
  tidyr::complete(country1 = all_countries, country2 = all_countries, fill = list(weight = 0)) %>%
  tidyr::pivot_wider(names_from = country2, values_from = weight, values_fill = 0)

#convert to matrix
adj_matrix <- as.matrix(adj_matrix_df[, -1])

#adding row names
rownames(adj_matrix) <- adj_matrix_df$country1

print(adj_matrix)
```

```{r}
dim(adj_matrix) #dimension
all(adj_matrix == t(adj_matrix)) #whether symmetric
#make the matrix symmetric
adj_matrix <- (adj_matrix + t(adj_matrix)) / 2
all(adj_matrix == t(adj_matrix)) 
```


```{r}
#normalize adjacency matrix (weights between 0 and 1)
adj_matrix <- adj_matrix / max(adj_matrix)
```



```{r}
model1 <- GERGM::gergm(adj_matrix ~ edges + triangles,
                       number_of_networks_to_simulate = 1000, #decreased sample number
                       thin = 1/10,
                       proposal_variance = 0.05,
                       MCMC_burnin = 500,                     
                       seed = 456,
                       convergence_tolerance = 0.01,
                       cores = 3)
summary(model1)
```





