---
title: "UN_assembly_proj"
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    
---

```{r setup, include=FALSE}
# ignore the errors
knitr::opts_chunk$set(error = TRUE)
set.seed(123)

library(dplyr)
library(tidyverse)
```


# Datasets
## UNGA

```{r}
#UNGA dataset
assembly <- readr::read_csv("2024_09_12_ga_resolutions_voting.csv")
head(assembly)
```


```{r}
unique(assembly['ms_name'])
```

Country name descrepancies: Yogoslavia republik, USSR, Ukranian SSR, Belorussian SSR, Turkey and Turkiye, East and West Germany, Former Yugoslav Republic of Macedonia, Serbia and Montenegro, etc.


```{r}
str(assembly)
```

```{r}
unique(assembly['modality'])
```

We chose years 2023 and 2024 for the Palestine Topic because of the events that happened in Gaza in October 2023.
```{r}
# working with the date variable
assembly <- assembly |> dplyr::mutate(date = lubridate::ymd(date))

data <- assembly %>% 
  dplyr::mutate(year = lubridate::year(date)) %>% #changing year variable
  filter(year %in% c(2023, 2024)) #including only 2023 and 2024
```


```{r}
#how many countries are in UN
unique(data['ms_code'])
```


```{r}
unique(data['title'])
```


```{r}
unique(data['subjects'])
```

**Related topics**: PALESTINE QUESTION, TERRITORIES OCCUPIED BY ISRAEL--SETTLEMENT POLICY, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS--REPORTS, TERRITORIES OCCUPIED BY ISRAEL--NATURAL RESOURCES, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS

```{r}
# include subject where words PALESTINE and ISRAEL are present
data <- data |> 
  filter(stringr::str_detect(subjects, "PALESTINE|ISRAEL"))
```


```{r}
#include only these variables
data <- data[c('ms_code', 'ms_vote', 'resolution', 
                                       'title')]
# deleting NV votes
data <- data |> 
  filter(ms_vote != "NV")
```
About 100 votes were NV


```{r}
#checking for duplicates
nrow(unique(data)) == nrow(data)
```
no duplicates


```{r}
#which resolutions are held
unique(data['title'])
```
Six titles overall that are about Palestine-Israel conflict.
**Seven** resolutions.
```{r}
data %>%
  group_by(resolution) %>%
  summarise(vote_count = n())
```


```{r}
data |> 
  filter(ms_code == 'ISR')
```
Israel voted 'No' in all seven resolutions.


### making network

```{r}
#Adjacency matrix
countries <- unique(data$ms_code)

n <- length(countries)
adj_matrix <- matrix(0, nrow = n, ncol = n, dimnames = list(countries, countries))

resolutions <- unique(data$resolution)
for (res in resolutions) {
  # Filter votes for the current resolution
  votes <- data |> filter(resolution == res)
  
  # Get pairs of countries that voted "Yes"
  yes_votes <- votes |> filter(ms_vote == "Y")
  yes_pairs <- combn(yes_votes$ms_code, 2, simplify = FALSE)
  
  # Increment matrix for "Yes" pairs
  for (pair in yes_pairs) {
    adj_matrix[pair[1], pair[2]] <- adj_matrix[pair[1], pair[2]] + 1
    adj_matrix[pair[2], pair[1]] <- adj_matrix[pair[2], pair[1]] + 1  # Symmetric
  }
}
```


Checking distribution of Yes votes
```{r}
#filtering only yes votes
yes_votes <- data |>
  filter(ms_vote == "Y")

# grouping and counting the votes
country_yes_counts <- yes_votes |>
  group_by(ms_code) |> 
  summarise(yes_count = n())

#making a table
country_yes_counts <- table(country_yes_counts$yes_count)

#visualizing the distribution
barplot(
  country_yes_counts,
  main = "Distribution of Yes Votes Across Countries",
  xlab = "Number of Yes Votes",
  ylab = "Frequency of Countries",
  col = "lightblue",
  border = "black"
)
```

I will work with two adjacency matrices. One without any threshold (adj_matrix2), and one with connections only if a country voted yes 5 times or more (adj_matrix3)

```{r}
adj_matrix2 <- ifelse(adj_matrix >= 1, 1, 0) #adj without threshold
adj_matrix3 <- ifelse(adj_matrix >= 5, 1, 0) #adj with threshold
```


## Democracy level

```{r}
# V-Dem project
democracy <- readr::read_csv("V-Dem-CY-Full+Others-v14.csv")
```

```{r}
democracy <- democracy |> 
  filter(year == 2023)

#leaving only needed columns
democracy <- democracy[c('country_text_id', 'v2x_polyarchy', 'v2x_libdem', 
                       'v2x_partipdem', 'v2x_delibdem', 'v2x_egaldem')]
```

**v2x_polyarchy** - To what extent is the ideal of electoral democracy in its fullest sense achieved?
**v2x_libdem** - To what extent is the ideal of liberal democracy achieved?
**v2x_partipdem** - To what extent is the ideal of participatory democracy achieved?
**v2x_delibdem** - To what extent is the ideal of deliberative democracy achieved?
**v2x_egaldem** - To what extent is the ideal of egalitarian democracy achieved? (rights are protected equally across all groups)


```{r}
#checking correlations
cor.test(democracy$v2x_polyarchy, democracy$v2x_partipdem, method = "pearson")
```

```{r}
cor.test(democracy$v2x_polyarchy, democracy$v2x_egaldem, method = "pearson")
```

Since they are highly correlated, we are choosing only electoral democracy score.
```{r}
democracy <- democracy[c('country_text_id', 'v2x_polyarchy')]
```


## Religion

```{r}
#importing the dataset
religion <- readr::read_csv('WRP_national.csv')
```

```{r}
#picking the most recent year
religion <- religion |> 
  filter(year == 2010)
```


```{r}
#listing religious groups
religion_columns <- c( "chrstgen", "judgen", "islmgen", "budgen", "zorogen", "hindgen", 
                      "sikhgen", "shntgen", "bahgen", "taogen", "jaingen", "confgen", 
                      "syncgen", "anmgen", "nonrelig", "othrgen")

#creating a variable with the most popular one
religion <- religion %>%
  rowwise() %>%
  mutate(
    largest_religion = religion_columns[which.max(c_across(all_of(religion_columns)))]
  ) %>%
  ungroup()

#selecting only needed columns
religion <- religion[c('name', 'largest_religion')]
```


```{r}
as.vector(religion['name'])
```
The data is not using ISO 3166-1 alpha-3 country codes. We have to match them manually:
```{r}
mapping <- data.frame(
  custom_code = c("USA", "CAN", "BHM", "CUB", "HAI", "DOM", "JAM", "TRI", "BAR", "DMA", 
                  "GRN", "SLU", "SVG", "AAB", "SKN", "MEX", "BLZ", "GUA", "HON", "SAL", 
                  "NIC", "COS", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
                  "BOL", "PAR", "CHL", "ARG", "URU", "UKG", "IRE", "NTH", "BEL", "LUX", 
                  "FRN", "MNC", "LIE", "SWZ", "SPN", "AND", "POR", "GMY", "POL", "AUS", 
                  "HUN", "CZR", "SLO", "ITA", "SNM", "MLT", "ALB", "MNG", "MAC", "CRO", 
                  "YUG", "BOS", "KOS", "SLV", "GRC", "CYP", "BUL", "MLD", "ROM", "RUS", 
                  "EST", "LAT", "LIT", "UKR", "BLR", "ARM", "GRG", "AZE", "FIN", "SWD", 
                  "NOR", "DEN", "ICE", "CAP", "STP", "GNB", "EQG", "GAM", "MLI", "SEN", 
                  "BEN", "MAA", "NIR", "CDI", "GUI", "BFO", "LBR", "SIE", "GHA", "TOG", 
                  "CAO", "NIG", "GAB", "CEN", "CHA", "CON", "DRC", "UGA", "KEN", "TAZ", 
                  "BUI", "RWA", "SOM", "DJI", "ETH", "ERI", "ANG", "MZM", "ZAM", "ZIM", 
                  "MAW", "SAF", "NAM", "LES", "BOT", "SWA", "MAG", "COM", "MAS", "SEY", 
                  "MOR", "ALG", "TUN", "LIB", "SUD", "IRN", "TUR", "IRQ", "EGY", "SYR", 
                  "LEB", "JOR", "ISR", "SAU", "YEM", "KUW", "BAH", "QAT", "UAE", "OMA", 
                  "AFG", "TKM", "TAJ", "KYR", "UZB", "KZK", "CHN", "TAW", "PRK", "ROK", 
                  "JPN", "IND", "BHU", "PAK", "BNG", "MYA", "SRI", "MAD", "NEP", "THI", 
                  "CAM", "LAO", "DRV", "MAL", "SIN", "BRU", "PHI", "INS", "ETM", "AUL", 
                  "PNG", "NEW", "VAN", "SOL", "KIR", "TUV", "FIJ", "TON", "NAU", "MSI", 
                  "PAL", "FSM", "WSM"),
  iso3c = c("USA", "CAN", "BHS", "CUB", "HTI", "DOM", "JAM", "TTO", "BRB", "DMA", 
            "GRD", "LCA", "VCT", "ATG", "KNA", "MEX", "BLZ", "GTM", "HND", "SLV", 
            "NIC", "CRI", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
            "BOL", "PRY", "CHL", "ARG", "URY", "GBR", "IRL", "NLD", "BEL", "LUX", 
            "FRA", "MCO", "LIE", "CHE", "ESP", "AND", "PRT", "DEU", "POL", "AUT", 
            "HUN", "CZE", "SVK", "ITA", "SMR", "MLT", "ALB", "MNE", "MKD", "HRV", 
            "YUG", "BIH", "XKX", "SVN", "GRC", "CYP", "BGR", "MDA", "ROU", "RUS", 
            "EST", "LVA", "LTU", "UKR", "BLR", "ARM", "GEO", "AZE", "FIN", "SWE", 
            "NOR", "DNK", "ISL", "CPV", "STP", "GNB", "GNQ", "GMB", "MLI", "SEN", 
            "BEN", "MAR", "NER", "CIV", "GIN", "BFA", "LBR", "SLE", "GHA", "TGO", 
            "CMR", "NGA", "GAB", "CAF", "TCD", "COG", "COD", "UGA", "KEN", "TZA", 
            "BDI", "RWA", "SOM", "DJI", "ETH", "ERI", "AGO", "MOZ", "ZMB", "ZWE", 
            "MWI", "ZAF", "NAM", "LSO", "BWA", "SWZ", "MDG", "COM", "MUS", "SYC", 
            "MAR", "DZA", "TUN", "LBY", "SDN", "IRN", "TUR", "IRQ", "EGY", "SYR", 
            "LBN", "JOR", "ISR", "SAU", "YEM", "KWT", "BHR", "QAT", "ARE", "OMN", 
            "AFG", "TKM", "TJK", "KGZ", "UZB", "KAZ", "CHN", "TWN", "PRK", "KOR", 
            "JPN", "IND", "BTN", "PAK", "BGD", "MMR", "LKA", "MDV", "NPL", "THA", 
            "KHM", "LAO", "VNM", "MYS", "SGP", "BRN", "PHL", "IDN", "TLS", "AUS", 
            "PNG", "NZL", "VUT", "SLB", "KIR", "TUV", "FJI", "TON", "NRU", "WSM", 
            "PLW", "FSM", "WSM")
)

#merging religion with mapping and update
religion <- religion |>
  left_join(mapping, by = c("name" = "custom_code")) |>
  mutate(name = ifelse(!is.na(iso3c), iso3c, name)) |>
  select(-iso3c)
```


```{r}
#which religious groups are the most popular
unique(religion['largest_religion'])
```

```{r}
# countries where majority of population is non-religious
religion |> 
  filter(largest_religion == 'nonrelig')
```



```{r}
#making network for non-threshold matrix
yes_graph1 <- igraph::graph_from_adjacency_matrix(adj_matrix2, 
                                                   mode = "undirected", 
                                                   weighted = FALSE)
```


```{r}
yes_graph1
```

```{r}
plot(yes_graph1, 
     vertex.label = igraph::V(yes_graph1)$name)
```

```{r}
snafun::is_connected(yes_graph1)
snafun::g_density(yes_graph1)
```


```{r}
# graph for threshold matrix
yes_graph2 <- igraph::graph_from_adjacency_matrix(adj_matrix3, 
                                                   mode = "undirected", 
                                                   weighted = FALSE)
yes_graph2
```

```{r}
plot(yes_graph2, 
     vertex.label = igraph::V(yes_graph2)$name)
```

```{r}
snafun::g_density(yes_graph2)
```


```{r}
# democracy index covariate
countries <- rownames(adj_matrix2)

node_df <- data.frame(country_text_id = countries)

# merging with democracy scores
node_df <- node_df |>
  left_join(democracy, by = "country_text_id")

# using mean scores to fill in missing values
node_df$v2x_polyarchy[is.na(node_df$v2x_polyarchy)] <- mean(node_df$v2x_polyarchy, na.rm = TRUE)

#merging with religion
names(religion)[1] <- "country_text_id" #renaming the country column
node_df <- node_df |>
  left_join(religion, by = "country_text_id")
```


```{r}
node_df[apply(is.na(node_df), 1, any), ]
```
Missing religion for Marshall Islands, Mauritania, Mongolia, Serbia, and South Sudan. They will be filled in manually with the data from [WorldPopulationReviw](https://worldpopulationreview.com/country-rankings/religion-by-country) that got data from CIA, UN, etc.
```{r}
#manually filling in the data
node_df <- node_df |>
  mutate(largest_religion = case_when(
    country_text_id == 'MHL' ~ 'chrstgen',
    country_text_id == 'MRT' ~ 'islmgen',
    country_text_id == 'MNG' ~ 'budgen',
    country_text_id == 'SRB' ~ 'chrstgen',
    country_text_id == 'SSD' ~ 'chrstgen',
    TRUE ~ largest_religion
  ))
```


```{r}
#checking if any NAs left
sum(is.na(node_df))
```



# Models

## No threshold network
```{r}
#network object
yes_net1 <- network::network(adj_matrix2, directed = FALSE, matrix.type = "adjacency")

#adding vertex attributes
network::set.vertex.attribute(yes_net1, "democracy_score", node_df$v2x_polyarchy)
network::set.vertex.attribute(yes_net1, "largest_religion", node_df$largest_religion)
```

```{r}
yes_net1
```

```{r}
plot(yes_net1,
     vertex.col = as.factor(network::get.vertex.attribute(yes_net1, "largest_religion")),
     main = "Network Visualization by Religion")

# Add a legend with religion names
legend("bottomleft",
       fill = 1:length(unique(network::get.vertex.attribute(yes_net1, "largest_religion"))),
       legend = unique(network::get.vertex.attribute(yes_net1, "largest_religion")),
       cex = 0.75,
       title = "Largest Religion")
```



```{r}
ergm::search.ergmTerms(keywords=c('binary','undirected'))
```

`gwdsp` captures the tendency for two nodes to share common neighbors, but unlike `gwesp`, it doesn't require these nodes to form triangles. This can work better in dense networks where clustering is dominated by shared neighbors rather than transitive triangles. **Didn't work**

 `density` and `transitivity` didn't work as well.
 
 

```{r}
model_yes1 <- ergm::ergm(yes_net1 ~ edges + degree1.5, 
                         control = ergm::control.ergm(MCMC.burnin = 1000,
                                                      MCMC.samplesize = 50000,
                                                      seed = 123,
                                                      MCMLE.maxit = 20,
                                                      parallel = 3,
                                                      parallel.type = "PSOCK"))

summary(model_yes1)
```
Ran for 72 minutes
`Degreepopularity` shows the propensity for nodes with high degrees (those already well-connected) to be more likely to gain additional edges (connections).
`Degreepopularity` is replaced automatically by degree1.5, which means the same thing. Thus, I replaced it in the codes as well.

It seems to be working but diagnostics were bad. Will try `gwdegree(0.5, cutoff = 150)` and `gwesp(decay=0.03, fixed = TRUE)`.

```{r}
model_yes2 <- ergm::ergm(yes_net1 ~ edges + degree1.5 + 
                           nodecov("democracy_score"), 
                         control = ergm::control.ergm(MCMC.burnin = 1000,
                                                      MCMC.samplesize = 50000,
                                                      seed = 123,
                                                      MCMLE.maxit = 20,
                                                      parallel = 3,
                                                      parallel.type = "PSOCK"))

summary(model_yes2)
```
Ran for 42 min

```{r}
table(node_df$largest_religion)
```
The religion categories are heavily unbalanced. May cause problems? --> nodematch did not run and nodefactor was running for hours (didn't finish it)

```{r}
node_df$largest_religion <- 
  ifelse(node_df$largest_religion %in% 
           c("anmggen", "budgen", "hindgen", "judgen", "nonrelig", 
             "shntgen", "syncgen", "anmgen"),"Other",
         node_df$largest_religion)

table(node_df$largest_religion)

#updating network covariate
network::set.vertex.attribute(yes_net1, "largest_religion", node_df$largest_religion)
```


```{r}
model_yes3 <- ergm::ergm(yes_net1 ~ edges + degree1.5 + 
                           nodecov("democracy_score") + 
                           nodematch("largest_religion"),
                         control = ergm::control.ergm(MCMC.burnin = 5000,
                                                      MCMC.samplesize = 100000,
                                                      seed = 123,
                                                      MCMC.interval = 100, # reduce autocorrelation
                                                      MCMLE.maxit = 25,
                                                      parallel = 3,
                                                      parallel.type = "PSOCK"))

summary(model_yes3)
```


```{r}
texreg::screenreg(list(model_yes1, model_yes2))
```


```{r}
#network object
yes_net2 <- network::network(adj_matrix3, directed = FALSE, matrix.type = "adjacency")

#adding vertex attributes
network::set.vertex.attribute(yes_net2, "democracy_score", node_df$v2x_polyarchy)
network::set.vertex.attribute(yes_net2, "largest_religion", node_df$largest_religion)
```

```{r}
yes_net2
```
```{r}
plot(yes_net2,
     vertex.col = as.factor(network::get.vertex.attribute(yes_net2, "largest_religion")),
     main = "Network Visualization by Religion")

legend("bottomleft",
       fill = 1:length(unique(network::get.vertex.attribute(yes_net2, "largest_religion"))),
       legend = unique(network::get.vertex.attribute(yes_net2, "largest_religion")),
       cex = 0.75,
       title = "Largest Religion")
```


```{r}
model_yes11 <- ergm::ergm(yes_net2 ~ edges + degree1.5, 
                         control = ergm::control.ergm(MCMC.burnin = 1000,
                                                      MCMC.samplesize = 50000,
                                                      seed = 123,
                                                      MCMLE.maxit = 20,
                                                      parallel = 3,
                                                      parallel.type = "PSOCK"))

summary(model_yes11)
```

```{r}
ergm::mcmc.diagnostics(model_yes11)
```
```{r}
igraph_net2 <- intergraph::asIgraph(yes_net2)

# Plot degree distribution
plot(igraph::degree_distribution(igraph_net2), type = "h",
     main = "Degree Distribution",
     xlab = "Degree", ylab = "Proportion of Nodes")
```



```{r}
#trying gwedegree instead of degree1.5 since it might be better at handling skewed distributions
model_yes12 <- ergm::ergm(yes_net2 ~ edges + gwdegree(0.5, cutoff = 150), 
                         control = ergm::control.ergm(MCMC.burnin = 1000,
                                                      MCMC.samplesize = 50000,
                                                      seed = 123,
                                                      MCMLE.maxit = 20,
                                                      parallel = 3,
                                                      parallel.type = "PSOCK"))

summary(model_yes12)
```





```{r}
model_yes13 <- ergm::ergm(yes_net2 ~ edges + degree1.5 + gwesp(decay=0.03, fixed = TRUE), 
                         control = ergm::control.ergm(MCMC.burnin = 1000,
                                                      MCMC.samplesize = 50000,
                                                      seed = 123,
                                                      MCMLE.maxit = 20,
                                                      MCMC.interval = 5000,
                                                      parallel = 3,
                                                      parallel.type = "PSOCK"))

summary(model_yes13)
```


```{r}
model_yes13 <- ergm::ergm(yes_net2 ~ edges + degree1.5 + nodecov("democracy_score") + 
                            nodematch("largest_religion"), 
                         control = ergm::control.ergm(MCMC.burnin = 1000,
                                                      MCMC.samplesize = 50000,
                                                      seed = 123,
                                                      MCMLE.maxit = 20,
                                                      MCMC.interval = 5000,
                                                      parallel = 3,
                                                      parallel.type = "PSOCK"))

summary(model_yes13)
```








I am not deleting the agreement term yet just in case.
## Same method as B. Kim et al (agreement term)


```{r}
adj_matrix_agree <- matrix(0, nrow = n, ncol = n, dimnames = list(countries, countries))

for (res in resolutions) {
  # Filter votes for the current resolution
  votes <- data |> filter(resolution == res)
  
  # Compare all pairs of countries
  for (i in 1:(nrow(votes) - 1)) {
    for (j in (i + 1):nrow(votes)) {
      country1 <- votes$ms_code[i]
      country2 <- votes$ms_code[j]
      vote1 <- votes$ms_vote[i]
      vote2 <- votes$ms_vote[j]
      
      # Calculate agreement score
      if (vote1 == vote2) {
        score <- 1  # Full agreement
      } else if ((vote1 == "Y" && vote2 == "A") || (vote1 == "A" && vote2 == "Y") ||
                 (vote1 == "N" && vote2 == "A") || (vote1 == "A" && vote2 == "N")) {
        score <- 0.5  # Partial agreement
      } else {
        score <- 0  # No agreement
      }
      
      # Update adjacency matrix
      adj_matrix_agree[country1, country2] <- adj_matrix_agree[country1, country2] + score
      adj_matrix_agree[country2, country1] <- adj_matrix_agree[country2, country1] + score  # Symmetric
    }
  }
}
```


```{r}
#round down for count ergm
adj_matrix_agree <- floor(adj_matrix_agree)
```



```{r}
#making network
agree_graph <- igraph::graph_from_adjacency_matrix(adj_matrix2,
                                                     mode = "undirected",
                                                     weighted = TRUE)
print(agree_graph)
```

```{r}
plot(agree_graph, 
     edge.width = igraph::E(agree_graph)$weight, 
     vertex.label = igraph::V(agree_graph)$name)
```

```{r}
print(agree_net)
```



The edge is this network is the level of agreement on votes. Weight - sum of agreement scores.


```{r}
igraph::is_connected(agree_graph)
igraph::edge_density(agree_graph)
```



```{r}
#network for agreement scores
agree_net <- network::network(adj_matrix_agree, directed = FALSE, matrix.type = "adjacency")
#edge attribute
network::set.edge.attribute(agree_net, "weight", as.vector(adj_matrix_agree[adj_matrix_agree > 0]))
#vertex attributes
network::set.vertex.attribute(agree_net, "democracy_score", node_df$v2x_polyarchy)
network::set.vertex.attribute(agree_net, "largest_religion", religion$largest_religion)
```


```{r}
model_agree1 <- ergm(agree_net ~ edges + nodecov("democracy_score"),
               response = "weight",      # the edge attribute
               reference = ~Poisson,
               control = ergm::control.ergm(MCMC.burnin = 5000,
                                            MCMC.samplesize = 10000,
                                            seed = 123,
                                            MCMLE.maxit = 20, #N of iterations
                                            parallel = 3,
                                            parallel.type = "PSOCK"))   

summary(model_agree1)
```


```{r}
model_agree2 <- ergm(agree_net ~ edges + nodecov("democracy_score") + 
                       nodematch("largest_religion"),
                     response = "weight",      # the edge attribute
                     reference = ~Poisson,
                     control = ergm::control.ergm(MCMC.burnin = 5000,
                                                  MCMC.samplesize = 10000,
                                                  seed = 123,
                                                  MCMLE.maxit = 20, #N of iterations
                                                  parallel = 3,
                                                  parallel.type = "PSOCK"))   

summary(model_agree2)
```


 
```{r}
model_agree3 <- ergm(agree_net ~ nonzero + sum + nodecov("democracy_score"),
                     response = "weight",      # the edge attribute
                     reference = ~Poisson, 
                     control = ergm::control.ergm(MCMC.burnin = 50,
                                                  MCMC.samplesize = 100,
                                                  seed = 123,
                                                  MCMLE.maxit = 20, #N of iterations
                                                  parallel = 3,
                                                  parallel.type = "PSOCK"))  

summary(model_agree3)
```
 
```{r}
texreg::screenreg(list(model_agree1, model_agree2, model_agree3))
```
 
 
