---
title: "UNGA_bipartite"
output:
  pdf_document:
    toc: true
    toc_depth: '3'
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE) # ignore the errors
set.seed(123) #set the seed for consistent results

#libraries
library(dplyr)
library(tidyverse)
```


# Datasets
## UNGA

```{r}
#UNGA dataset
assembly <- readr::read_csv("2024_09_12_ga_resolutions_voting.csv")
head(assembly)
```
Country name descrepancies: Yogoslavia republik, USSR, Ukranian SSR, Belorussian SSR, Turkey and Turkiye, East and West Germany, Former Yugoslav Republic of Macedonia, Serbia and Montenegro, etc.


```{r}
unique(assembly['modality'])
```

We chose years 2023 and 2024 for the Palestine Topic because of the events that happened in Gaza in October 2023.
```{r}
# working with the date variable
assembly <- assembly |> dplyr::mutate(date = lubridate::ymd(date))

data <- assembly %>% 
  dplyr::mutate(year = lubridate::year(date)) %>% #changing year variable
  filter(year %in% c(2023, 2024)) #including only 2023 and 2024
```


```{r}
#how many countries are in UN
unique(data['ms_code'])
```


```{r}
unique(data['title'])
```

```{r}
unique(data['subjects'])
```

**Related topics**: PALESTINE QUESTION, TERRITORIES OCCUPIED BY ISRAEL--SETTLEMENT POLICY, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS--REPORTS, TERRITORIES OCCUPIED BY ISRAEL--NATURAL RESOURCES, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS
```{r}
# include subject where words PALESTINE and ISRAEL are present
data <- data |> 
  filter(stringr::str_detect(subjects, "PALESTINE|ISRAEL"))
```


```{r}
#include only these variables
data <- data[c('ms_code', 'ms_vote', 'resolution', 
                                       'title')]
# deleting NV votes
data <- data |> 
  filter(ms_vote != "NV")
```
About 100 votes were NV


```{r}
#checking for duplicates
nrow(unique(data)) == nrow(data)
```
no duplicates

```{r}
#which resolutions are held
unique(data['title'])
```

Six titles overall that are about Palestine-Israel conflict.
**Seven** resolutions.
```{r}
data |>
  group_by(resolution) |>
  summarise(vote_count = n())
```

```{r}
data |> 
  filter(ms_code == 'ISR')
```
Israel voted 'No' in all seven resolutions.


```{r}
#sorting alphabetically
data <- data |> 
  arrange(ms_code)
```


```{r}
write.csv(data, file = "data.csv", row.names = FALSE)
```




### Making a Bipartite network
While unimodal networks can also be represented by adjacency matrices, bipartite networks require **incidence matrices**.

```{r}
incidence_matrix_df <- data %>%
  filter(ms_vote == 'Y') %>%                 # Filter Yes votes
  select(ms_code, resolution, ms_vote) %>%      # Select relevant columns
  mutate(value = 1) %>%                # Assign value 1 for edges
  pivot_wider(names_from = resolution, # Create columns for resolutions
              values_from = value,
              values_fill = 0)         # Fill missing values with 0

# Convert to a matrix
incidence_matrix <- as.matrix(incidence_matrix_df[,-1])  # Exclude country names
colnames(incidence_matrix) <- NULL
```




```{r}
data$vote_binary <- ifelse(data$ms_vote == "Y", 1, 0)

# Create the incidence matrix
library(tidyr)
incidence_matrix_df <- data %>%
  select(ms_code, resolution, vote_binary) %>%
  pivot_wider(names_from = resolution, values_from = vote_binary, values_fill = 0)

incidence_matrix <- as.matrix(incidence_matrix_df[,-1])  # Exclude country names
colnames(incidence_matrix) <- NULL
print(incidence_matrix)
```


```{r}
any(is.na(incidence_matrix))
```


```{r}
#matrix dimensions
dim(incidence_matrix)
```


```{r}
UNGA <- network::network(incidence_matrix, directed = FALSE, bipartite = TRUE)
UNGA
```


```{r}
network::set.vertex.attribute(UNGA, "bipartite", value = rep(190, 190), v = 1:190)
UNGA
```

```{r}
# Degree partition 1 (countries)
summary(UNGA ~ b1degree(1:7))
# Degree partition 2 (resolutions)
summary(UNGA ~ b2degree(1:190))
```



## Democracy Data

```{r}
# V-Dem project
democracy <- readr::read_csv("V-Dem-CY-Full+Others-v14.csv")
```

```{r}
#choosing the latest available year
democracy <- democracy |> 
  filter(year == 2023)

#leaving only needed columns
democracy <- democracy[c('country_text_id', 'v2x_polyarchy', 'v2x_libdem', 
                       'v2x_partipdem', 'v2x_delibdem', 'v2x_egaldem')]
```
**v2x_polyarchy** - To what extent is the ideal of electoral democracy in its fullest sense achieved?
**v2x_libdem** - To what extent is the ideal of liberal democracy achieved?
**v2x_partipdem** - To what extent is the ideal of participatory democracy achieved?
**v2x_delibdem** - To what extent is the ideal of deliberative democracy achieved?
**v2x_egaldem** - To what extent is the ideal of egalitarian democracy achieved? (rights are protected equally across all groups)

```{r}
#checking correlations
cor.test(democracy$v2x_polyarchy, democracy$v2x_partipdem, method = "pearson")
```

```{r}
cor.test(democracy$v2x_polyarchy, democracy$v2x_egaldem, method = "pearson")
```
Since they are highly correlated, we are choosing only electoral democracy score.
```{r}
democracy <- democracy[c('country_text_id', 'v2x_polyarchy')]
```

```{r}
#arranging countries alphabetically
democracy <- democracy |> 
  arrange(country_text_id)
```



## Religion Data
```{r}
#importing the dataset
religion <- readr::read_csv('WRP_national.csv')
```

```{r}
#picking the most recent year
religion <- religion |> 
  filter(year == 2010)
```


```{r}
#listing religious groups
religion_columns <- c( "chrstgen", "judgen", "islmgen", "budgen", "zorogen", "hindgen", 
                      "sikhgen", "shntgen", "bahgen", "taogen", "jaingen", "confgen", 
                      "syncgen", "anmgen", "nonrelig", "othrgen")

#creating a variable with the most popular one (highest population)
religion <- religion %>%
  rowwise() %>%
  mutate(
    largest_religion = religion_columns[which.max(c_across(all_of(religion_columns)))]
  ) %>%
  ungroup()

#selecting only needed columns
religion <- religion[c('name', 'largest_religion')]
```

```{r}
as.vector(religion['name'])
```


The data is not using ISO 3166-1 alpha-3 country codes. We have to match them manually:
```{r}
mapping <- data.frame(
  custom_code = c("USA", "CAN", "BHM", "CUB", "HAI", "DOM", "JAM", "TRI", "BAR", "DMA", 
                  "GRN", "SLU", "SVG", "AAB", "SKN", "MEX", "BLZ", "GUA", "HON", "SAL", 
                  "NIC", "COS", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
                  "BOL", "PAR", "CHL", "ARG", "URU", "UKG", "IRE", "NTH", "BEL", "LUX", 
                  "FRN", "MNC", "LIE", "SWZ", "SPN", "AND", "POR", "GMY", "POL", "AUS", 
                  "HUN", "CZR", "SLO", "ITA", "SNM", "MLT", "ALB", "MNG", "MAC", "CRO", 
                  "YUG", "BOS", "KOS", "SLV", "GRC", "CYP", "BUL", "MLD", "ROM", "RUS", 
                  "EST", "LAT", "LIT", "UKR", "BLR", "ARM", "GRG", "AZE", "FIN", "SWD", 
                  "NOR", "DEN", "ICE", "CAP", "STP", "GNB", "EQG", "GAM", "MLI", "SEN", 
                  "BEN", "MAA", "NIR", "CDI", "GUI", "BFO", "LBR", "SIE", "GHA", "TOG", 
                  "CAO", "NIG", "GAB", "CEN", "CHA", "CON", "DRC", "UGA", "KEN", "TAZ", 
                  "BUI", "RWA", "SOM", "DJI", "ETH", "ERI", "ANG", "MZM", "ZAM", "ZIM", 
                  "MAW", "SAF", "NAM", "LES", "BOT", "SWA", "MAG", "COM", "MAS", "SEY", 
                  "MOR", "ALG", "TUN", "LIB", "SUD", "IRN", "TUR", "IRQ", "EGY", "SYR", 
                  "LEB", "JOR", "ISR", "SAU", "YEM", "KUW", "BAH", "QAT", "UAE", "OMA", 
                  "AFG", "TKM", "TAJ", "KYR", "UZB", "KZK", "CHN", "TAW", "PRK", "ROK", 
                  "JPN", "IND", "BHU", "PAK", "BNG", "MYA", "SRI", "MAD", "NEP", "THI", 
                  "CAM", "LAO", "DRV", "MAL", "SIN", "BRU", "PHI", "INS", "ETM", "AUL", 
                  "PNG", "NEW", "VAN", "SOL", "KIR", "TUV", "FIJ", "TON", "NAU", "MSI", 
                  "PAL", "FSM", "WSM"),
  iso3c = c("USA", "CAN", "BHS", "CUB", "HTI", "DOM", "JAM", "TTO", "BRB", "DMA", 
            "GRD", "LCA", "VCT", "ATG", "KNA", "MEX", "BLZ", "GTM", "HND", "SLV", 
            "NIC", "CRI", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
            "BOL", "PRY", "CHL", "ARG", "URY", "GBR", "IRL", "NLD", "BEL", "LUX", 
            "FRA", "MCO", "LIE", "CHE", "ESP", "AND", "PRT", "DEU", "POL", "AUT", 
            "HUN", "CZE", "SVK", "ITA", "SMR", "MLT", "ALB", "MNE", "MKD", "HRV", 
            "YUG", "BIH", "XKX", "SVN", "GRC", "CYP", "BGR", "MDA", "ROU", "RUS", 
            "EST", "LVA", "LTU", "UKR", "BLR", "ARM", "GEO", "AZE", "FIN", "SWE", 
            "NOR", "DNK", "ISL", "CPV", "STP", "GNB", "GNQ", "GMB", "MLI", "SEN", 
            "BEN", "MAR", "NER", "CIV", "GIN", "BFA", "LBR", "SLE", "GHA", "TGO", 
            "CMR", "NGA", "GAB", "CAF", "TCD", "COG", "COD", "UGA", "KEN", "TZA", 
            "BDI", "RWA", "SOM", "DJI", "ETH", "ERI", "AGO", "MOZ", "ZMB", "ZWE", 
            "MWI", "ZAF", "NAM", "LSO", "BWA", "SWZ", "MDG", "COM", "MUS", "SYC", 
            "MAR", "DZA", "TUN", "LBY", "SDN", "IRN", "TUR", "IRQ", "EGY", "SYR", 
            "LBN", "JOR", "ISR", "SAU", "YEM", "KWT", "BHR", "QAT", "ARE", "OMN", 
            "AFG", "TKM", "TJK", "KGZ", "UZB", "KAZ", "CHN", "TWN", "PRK", "KOR", 
            "JPN", "IND", "BTN", "PAK", "BGD", "MMR", "LKA", "MDV", "NPL", "THA", 
            "KHM", "LAO", "VNM", "MYS", "SGP", "BRN", "PHL", "IDN", "TLS", "AUS", 
            "PNG", "NZL", "VUT", "SLB", "KIR", "TUV", "FJI", "TON", "NRU", "WSM", 
            "PLW", "FSM", "WSM")
)

#merging religion with mapping
religion <- religion |>
  left_join(mapping, by = c("name" = "custom_code")) |>
  mutate(name = ifelse(!is.na(iso3c), iso3c, name)) |>
  select(-iso3c)
```


```{r}
#which religious groups are the most popular
unique(religion['largest_religion'])
```

```{r}
# countries where majority of population is non-religious
religion |> 
  filter(largest_religion == 'nonrelig')
```

```{r}
#sorting alphabetically
religion <- religion |> 
  arrange(name)
```


## US Aid Data

Data source: https://results.usaid.gov/results/country?fiscalYear=2023
```{r}
usaid <- readxl::read_excel("d2r_complete_data.xlsx")
```

```{r}
#choosing the latest year
usaid <- usaid %>% 
  filter(fiscal_year == 2022) #including only 2023 and 2024

head(usaid)
```

```{r}
unique(usaid['country_name'])
```

```{r}
unique(usaid['sector_name'])
```

```{r}
#summing the values
usaid <- usaid %>% 
  group_by(country_name) %>%
  summarize(total_disbursements = sum(disbursements, na.rm = TRUE))
```


```{r}
country_names <- usaid$country_name
#converting country names to iso3c country codes
usaid$country_text_id <- countrycode::countrycode(country_names, 
                                              origin = "country.name", 
                                              destination = "iso3c")

usaid <- usaid[c("country_text_id", "total_disbursements")]
head(usaid)
```

```{r}
#dropping NAs
usaid <- drop_na(usaid)
```

```{r}
#sorting alphabetically
usaid <- usaid |> 
  arrange(country_text_id)
```


## GDP Dataset

```{r}
#importing GDP dataset
gdp <- readr::read_csv('gdp_data.csv')
```
```{r}
#renaming the column
gdp$country_text_id <- gdp$`Country Code`

#dropping unnecessary columns
gdp$`Country Code` <- NULL
gdp$...1 <- NULL
```


## Covariate dataset

```{r}
# democracy index covariate
countries <- incidence_matrix_df$ms_code

node_df <- data.frame(country_text_id = countries)

#merging with religion
names(religion)[1] <- "country_text_id" #renaming the country column
node_df <- node_df |>
  left_join(religion, by = "country_text_id")

# merging with democracy scores
node_df <- node_df |>
  left_join(democracy, by = "country_text_id")

# using mean scores to fill in missing values
node_df$v2x_polyarchy[is.na(node_df$v2x_polyarchy)] <- mean(node_df$v2x_polyarchy, na.rm = TRUE)

#merging USAID data into node_df
node_df <- node_df |>
  left_join(usaid, by = "country_text_id")

#filling missing USAID values with 0
node_df$total_disbursements[is.na(node_df$total_disbursements)] <- 0

#merging with GDP
node_df <- node_df |>
  left_join(gdp, by = "country_text_id")
```


```{r}
node_df[apply(is.na(node_df), 1, any), ]
```

Missing religion for Marshall Islands, Mauritania, Mongolia, Serbia, and South Sudan. They will be filled in manually with the data from [WorldPopulationReviw](https://worldpopulationreview.com/country-rankings/religion-by-country) that got data from CIA, UN, etc.
```{r}
#manually filling in the data
node_df <- node_df |>
  mutate(largest_religion = case_when(
    country_text_id == 'MHL' ~ 'chrstgen',
    country_text_id == 'MRT' ~ 'islmgen',
    country_text_id == 'MNG' ~ 'budgen',
    country_text_id == 'SRB' ~ 'chrstgen',
    country_text_id == 'SSD' ~ 'chrstgen',
    TRUE ~ largest_religion))
```


```{r}
#matching node_df rows with the rows of incidence matrix
node_df <- node_df[match(incidence_matrix_df$ms_code, node_df$country_text_id), ]
```

We have decided to make religion variable binomial:
```{r}
#dummifying religion column. If country is islamic, the value = 1. If other - 0.
node_df$if_islamic <- ifelse(node_df$largest_religion == "islmgen", 1, 0)
node_df$largest_religion <- NULL
```


```{r}
vertex_name <- node_df$country_text_id
resolutions <- c('ARESES-1021', 'ARES78170', 'ARESES-1023', 
                      'ARES7876', 'ARESES-1022', 'ARES7877', 'ARES7878') #resolution names

vertex_name <- append(vertex_name, resolutions)
vertex_name
```


```{r}
#setting vertex attributes
network::set.vertex.attribute(UNGA, "vertex.names", vertex_name)
network::set.vertex.attribute(UNGA, "democracy_score", node_df$v2x_polyarchy, v = 1:190)
network::set.vertex.attribute(UNGA, "islamic", node_df$if_islamic, v = 1:190)
network::set.vertex.attribute(UNGA, "USAid", node_df$total_disbursements, v = 1:190)
network::set.vertex.attribute(UNGA, "GDP", node_df$gdp, v = 1:190)
```



```{r}
network::set.vertex.attribute(UNGA, "bipartite", c(rep(0, 190), rep(1, 7)))
```


```{r}
# Degree partition 1 (countries)
summary(UNGA ~ b1degree(1:7))
# Degree partition 2 (resolutions)
summary(UNGA ~ b2degree(1:190))
```


```{r}
bipartite_attr <- network::get.vertex.attribute(UNGA, "bipartite")
print(bipartite_attr)  # This should show 0 for countries and 1 for resolutions.
```



```{r}
# Identify indices of resolutions
resolution_indices <- which(bipartite_attr == 1)

# Extract degrees for resolutions
resolution_degrees <- sna::degree(UNGA, cmode = "indegree")[resolution_indices]

# Get resolution names
resolution_names <- network::get.vertex.attribute(UNGA, "vertex.names")[resolution_indices]

# Create a dataframe with resolution-specific edge counts
resolution_summary <- data.frame(
  Resolution = resolution_names,
  Edges = resolution_degrees
)

# Print the summary
print(resolution_summary)
```
With the exception of resolution ARES78170 and ARESES-1021, the resolutions tend to have a similar number of votes in favor. Most countries voted in favor of all resolutions with the exception of ARES78170 as it only received 86 votes in favor out of 190 possible ones. The resolution with the highest amount of votes is ARES7877

```{r}
# Identify indices of countries
resolution_indices <- which(bipartite_attr == 0)

# Extract degrees for countries
resolution_degrees <- sna::degree(UNGA, cmode = "indegree")[resolution_indices]

# Get country names
resolution_names <- network::get.vertex.attribute(UNGA, "vertex.names")[resolution_indices]

# Create a dataframe with country-specific edge counts
resolution_summary <- data.frame(
  Country = resolution_names,
  Edges = resolution_degrees
)

# Print the summary
print(resolution_summary)
```
```{r}
ggplot2::ggplot(resolution_summary, aes(x=Edges)) +
    ggplot2::geom_density() + ggplot2::ggtitle("Distribution of Votes in Favor of Resolutions") 
```

The notable peak around 6-7 edges, indicating that many countries tend to vote in favor of most or all resolutions (6-7 out of 7 possible resolutions). There's relatively low density between 0-2 edges, showing that very few countries did not vote in favor or did so for only a few resolutions. There's a gradual increase in density starting around 4 edges, with the steepest increase occurring between 5-6 edges. This indicates that the most common pattern is for countries to vote in favor of a majority of resolutions.
```{r}
#Network's density
snafun::g_density(UNGA)
```
The high density reveals that our network is quite dense as 72% of all possible connections in this network exist.

Since we are dealing with a bipartite network, to be able to measure other things such as transitivity and subgroups we will project the network and make it unipartite. Note: this is only done for this purpose, for the rest of the analysis we will continue using our bipartite network 

```{r}
UNGA_i <- snafun::to_igraph(UNGA)
projected_UNGA <- igraph::bipartite_projection(UNGA_i)
projected_UNGA


```
As we can see from the number of nodes and edges, the first projection is our countries one
```{r}
country_network <- projected_UNGA$proj1
country_network
```

```{r}
snafun::extract_all_vertex_attributes(country_network) 
```

We proceed with our network measures.
```{r}
snafun::g_summary(country_network)
```
The transitivity score of our network is extremely large, indicating that if country A and B vote similarly (both in favor) on some resolutions, and B and C vote similarly on some resolutions, then it's almost certain (98.4% of the time) that A and C also vote similarly. The high transitivity indicates high consistancy in voting patterns in resolutions, and a high tendency of voting in cohesive groups.

Looking at the density of the network we can see that after projection it increased from 72.1% to 84.1%. This makes sense as when projecting a lot of countries get connected even when they share one vote. The increase to 84.1% in the projected country-country network means that 84.1% of all possible pairs of countries share at least one common "yes" vote. 

The dyad census reveals that there are 15103 mutual edges in this network (equivalent to number of edges in this network since undirected) while the null value of 2852 represents the number of edges that could have been formed. This once again reveals that our network is highly connected as mutual edges are much larger than null. 

There are 14 isolates in our network. 14 countries did not vote in favor for any of the resolutions. The following code displays the country codes of the isolates.

```{r}
snafun::extract_isolates(country_network)
```
Cameroon, Federate Sates of Micronesia, Israel, Kiribati, Liberia, Marshall Islands, Nauru, Palau, Papua New Guinea, Paraguay, Togo, Tonga, and the United States did not vote in favor of any reolutions. 

```{r}
snafun::plot_centralities(country_network)
```
Betweeness: There is relatively more variability in this score in comparison to the others. The points with a between score of 0 are isolates. A lot of countries have the highest score of around 2.2.      

Closeness score measures the average shorted distance between all vertices. The very narrow range (between ~0.0044 and 0.0057) indicates that closeness scores tend to be similar between all points. Only one paricular country stands out in this plot as it appears to have a relatively lower closeness score (we will look more into this later). 

Eccentricity measures the maximum number of nodes that country have to go through to reach every other country. Most countries have an eccentricity score of 1 or 2, the low values are not surprising considering how interconnected our network is. Once again the isolates of this graph can be spotted by the fact that their eccentricity scores are 0. 

The degree distribution is what we expected based on our high density score. Most countries tend to have really large degrees (150-175). The 14 isolates can be spotted on the left side of this graph. 



```{r}
closeness_scores <- snafun::v_closeness(country_network)
# Find minimum closeness score
min_country <- names(which.min(closeness_scores[!is.na(closeness_scores)])) # excluding isolates (NAs)
min_score <- min(closeness_scores, na.rm=TRUE)

# Print results
print(paste("Country with lowest closeness:", min_country))
print(paste("Closeness score:", round(min_score, 6)))
```
Checking for communities 
```{r}
walktrap <- snafun::extract_comm_walktrap(country_network)

# check the modularity
igraph::modularity(walktrap)

# check which community each vertex belongs to
igraph::membership(walktrap) # ex: 0.45

snafun::plot(walktrap, country_network)
```
Here we remove isoltes:

```{r}
country_no_isolates <- snafun::remove_isolates(country_network)

walktrap <- snafun::extract_comm_walktrap(country_no_isolates)

# check the modularity
igraph::modularity(walktrap)

# check which community each vertex belongs to
igraph::membership(walktrap) # ex: 0.45

snafun::plot(walktrap, country_no_isolates)
```
```{r}
girvan <- snafun::extract_comm_girvan(country_network)

# check the modularity
igraph::modularity(girvan)

# check which community each vertex belongs to
igraph::membership(girvan)

snafun::plot(girvan, country_network)
```

```{r}
girvan <- snafun::extract_comm_girvan(country_no_isolates)

# check the modularity
igraph::modularity(girvan)

# check which community each vertex belongs to
igraph::membership(girvan)

snafun::plot(girvan, country_no_isolates)
```



```{r}
louvain <- snafun::extract_comm_louvain(country_no_isolates)

# check the modularity
igraph::modularity(louvain) 

# checking which community each node belongs to
igraph::membership(louvain)

snafun::plot(louvain, country_no_isolates)
```


# Model
Hypothesis 1. The popularity effects; some resolutions are more popular than others in a sense that more countries vote in favor of them. For instance some countries may care more about humanitarian issues rather than about territorial disputes. Some resolutions maybe more extreme than others, so if a country votes for it, it condemns Israel more **b2star**, **b2sociality(nodes=-1)**

**gwb2dsp**. - how many countries voted same way 
whether two countries voted similarly - **gwb1dsp**.


```{r}
ergm::search.ergmTerms(keywords=c('bipartite','undirected'))
```



```{r}
# Model 1. Just edges
model1 <-ergm::ergm(UNGA ~ edges,
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model1)
```


```{r}
#Model 2. Adding b2star(2)
model2 <-ergm::ergm(UNGA ~ edges + b2star(2),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model2)
```


```{r}
ergm::mcmc.diagnostics(model2)
```

```{r}
#table with models
texreg::screenreg(list(model1, model2))
```


```{r}
# Same as model 2 but trying with constraints
#model22 <-ergm::ergm(UNGA ~ edges + b2star(2),
#                    constraints = ~bd(minout = 0, maxout = c(rep(7, 176), rep(Inf, 7))),
#                    control = ergm::control.ergm(MCMC.burnin = 5000,
#                                                 MCMC.samplesize = 50000,
#                                                 seed = 123,
#                                                 MCMLE.maxit = 50,
 #                                                parallel = 3,
 #                                                parallel.type = "PSOCK"))
#summary(model22)
```
```{r}
#ergm::mcmc.diagnostics(model22)
```


```{r}
summary(UNGA ~ edges + b2star(2) + gwb1dsp)
```



gwb1dsp
```{r}
# Model 3. Adding gwb1dsp
model3 <-ergm::ergm(UNGA ~ edges + b2star(2) + b1degree(0),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 15,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model3)
```


```{r}
ergm::mcmc.diagnostics(model3)
```





```{r}
#table with models
texreg::screenreg(list(model1, model2, model3))
```

```{r}
# MCMC diagnostics of model3
ergm::mcmc.diagnostics(model3)
```


```{r}
# Model 4. Adding democracy score
model4 <-ergm::ergm(UNGA ~ edges + b2star(2) + 
                      b1nodematch("democracy_score", diff=TRUE),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model4)
```


```{r}
ergm::mcmc.diagnostics(model4)
```


```{r}
# Model 5. Adding religion
model5 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model5)
```


Trying balanced religion:
Muslim country - 1
```{r}
node_df$religion_balanced <- 
  ifelse(node_df$largest_religion %in% 
           c("anmggen", "budgen", "hindgen", "judgen", "nonrelig", 
             "shntgen", "syncgen", "anmgen"),"other",
         node_df$largest_religion)

table(node_df$religion_balanced)

#updating network covariate
network::set.vertex.attribute(UNGA, "religion_b", node_df$religion_balanced)
```


```{r}
#Same as model 5 but with more balanced religion
model52 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion_b"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model52)
```


```{r}
texreg::screenreg(list(model1, model2, model3, model4, model5))
```


If religion_b is still not significant, continue with `religion`.

```{r}
#Adding US Aid
model6 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion") + 
                      b1cov("USAid"),
                    control = ergm::control.ergm(MCMC.burnin = 10000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 15,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model6)
```


```{r}
#Adding GDP
model7 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion") + 
                      b1cov("USAid") + b1cov("GDP"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 12,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model7)
```


```{r}
#table with models
texreg::screenreg(list(model1, model2, model3, model4, model5, model6, model7))
```

```{r}
ergm::mcmc.diagnostics(model7)
```



```{r}
#Adding gwb1nsp term
model8 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2sociality(nodes=-1) + 
                      gwb1nsp(0, TRUE) + 
                      b1cov("democracy_score") + b1nodematch("religion") + 
                      b1cov("USAid") + b1cov("GDP"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model8)
```




# Trial

```{r}
mdata <- matrix(
  c(1, 1, 1, 1,
    1, 1, 0, 0,
    1, 1, 1, 0,
    1, 1, 0, 0,
    1, 1, 0, 1,
    0, 1, 1, 1,
    0, 0, 1, 1,
    1, 0, 1, 1,
    0, 0, 1, 1,
    0, 0, 1, 1), 
  nrow = 10,  # Number of rows
  ncol = 4,   # Number of columns
  byrow = TRUE # Fill matrix row by row
)

# Print the matrix
print(mdata)
```


```{r}
kidsnet <- network::network(mdata, directed = FALSE, bipartite = TRUE)
kidsnet
```

```{r}
network::set.vertex.attribute(kidsnet, "bipartite", value = rep(10, 10), v = 1:10)
kidsnet
```

```{r}
# Degree partition 1 (kids)
summary(kidsnet ~ b1degree(1:10))
# Degree partition 2 (play-dates)
summary(kidsnet ~ b2degree(1:10))
```

```{r}
Age <- c(11, 11, 10, 12, 11, 10, 13, 11, 10, 12)

network::set.vertex.attribute(kidsnet, "Age", Age, v = 1:10)
#network::set.vertex.attribute(kidsnet, "bipartite", value = rep(10, 10), v = 1:10)
network::get.vertex.attribute(kidsnet, "Age")
```


```{r}
# Degree partition 1 (kids)
summary(kidsnet ~ b1degree(1:10))
# Degree partition 2 (play-dates)
summary(kidsnet ~ b2degree(1:10))
```



