---
title: "UNGA_bipartite"
output: 
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE) # ignore the errors
set.seed(123) #set the seed for consistent results

#libraries
library(dplyr)
library(tidyverse)
```


# Datasets
## UNGA

```{r}
#UNGA dataset
assembly <- readr::read_csv("2024_09_12_ga_resolutions_voting.csv")
head(assembly)
```
Country name descrepancies: Yogoslavia republik, USSR, Ukranian SSR, Belorussian SSR, Turkey and Turkiye, East and West Germany, Former Yugoslav Republic of Macedonia, Serbia and Montenegro, etc.


```{r}
unique(assembly['modality'])
```

We chose years 2023 and 2024 for the Palestine Topic because of the events that happened in Gaza in October 2023.
```{r}
# working with the date variable
assembly <- assembly |> dplyr::mutate(date = lubridate::ymd(date))

data <- assembly %>% 
  dplyr::mutate(year = lubridate::year(date)) %>% #changing year variable
  filter(year %in% c(2023, 2024)) #including only 2023 and 2024
```


```{r}
#how many countries are in UN
unique(data['ms_code'])
```


```{r}
unique(data['title'])
```

```{r}
unique(data['subjects'])
```

**Related topics**: PALESTINE QUESTION, TERRITORIES OCCUPIED BY ISRAEL--SETTLEMENT POLICY, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS--REPORTS, TERRITORIES OCCUPIED BY ISRAEL--NATURAL RESOURCES, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS
```{r}
# include subject where words PALESTINE and ISRAEL are present
data <- data |> 
  filter(stringr::str_detect(subjects, "PALESTINE|ISRAEL"))
```


```{r}
#include only these variables
data <- data[c('ms_code', 'ms_vote', 'resolution', 
                                       'title')]
# deleting NV votes
data <- data |> 
  filter(ms_vote != "NV")
```
About 100 votes were NV


```{r}
#checking for duplicates
nrow(unique(data)) == nrow(data)
```
no duplicates

```{r}
#which resolutions are held
unique(data['title'])
```

Six titles overall that are about Palestine-Israel conflict.
**Seven** resolutions.
```{r}
data |>
  group_by(resolution) |>
  summarise(vote_count = n())
```

```{r}
data |> 
  filter(ms_code == 'ISR')
```
Israel voted 'No' in all seven resolutions.


```{r}
#sorting alphabetically
data <- data |> 
  arrange(ms_code)
```



### Making a Bipartite network
While unimodal networks can also be represented by adjacency matrices, bipartite networks require **incidence matrices**.

```{r}
incidence_matrix_df <- data %>%
  filter(ms_vote == 'Y') %>%                 # Filter Yes votes
  select(ms_code, resolution) %>%      # Select relevant columns
  mutate(value = 1) %>%                # Assign value 1 for edges
  pivot_wider(names_from = resolution, # Create columns for resolutions
              values_from = value,
              values_fill = 0)         # Fill missing values with 0

# Convert to a matrix
incidence_matrix <- as.matrix(incidence_matrix_df[,-1])  # Exclude country names
colnames(incidence_matrix) <- NULL
```

```{r}
incidence_matrix
```

```{r}
any(is.na(incidence_matrix))
```


```{r}
#matrix dimensions
dim(incidence_matrix)
```


```{r}
UNGA <- network::network(incidence_matrix, directed = FALSE, bipartite = TRUE)
UNGA
```


```{r}
network::set.vertex.attribute(UNGA, "bipartite", value = rep(176, 176), v = 1:176)
UNGA
```

```{r}
# Degree partition 1 (countries)
summary(UNGA ~ b1degree(1:7))
# Degree partition 2 (resolutions)
summary(UNGA ~ b2degree(1:176))
```



## Democracy Data

```{r}
# V-Dem project
democracy <- readr::read_csv("V-Dem-CY-Full+Others-v14.csv")
```

```{r}
#choosing the latest available year
democracy <- democracy |> 
  filter(year == 2023)

#leaving only needed columns
democracy <- democracy[c('country_text_id', 'v2x_polyarchy', 'v2x_libdem', 
                       'v2x_partipdem', 'v2x_delibdem', 'v2x_egaldem')]
```
**v2x_polyarchy** - To what extent is the ideal of electoral democracy in its fullest sense achieved?
**v2x_libdem** - To what extent is the ideal of liberal democracy achieved?
**v2x_partipdem** - To what extent is the ideal of participatory democracy achieved?
**v2x_delibdem** - To what extent is the ideal of deliberative democracy achieved?
**v2x_egaldem** - To what extent is the ideal of egalitarian democracy achieved? (rights are protected equally across all groups)

```{r}
#checking correlations
cor.test(democracy$v2x_polyarchy, democracy$v2x_partipdem, method = "pearson")
```

```{r}
cor.test(democracy$v2x_polyarchy, democracy$v2x_egaldem, method = "pearson")
```
Since they are highly correlated, we are choosing only electoral democracy score.
```{r}
democracy <- democracy[c('country_text_id', 'v2x_polyarchy')]
```

```{r}
#arranging countries alphabetically
democracy <- democracy |> 
  arrange(country_text_id)
```



## Religion Data
```{r}
#importing the dataset
religion <- readr::read_csv('WRP_national.csv')
```

```{r}
#picking the most recent year
religion <- religion |> 
  filter(year == 2010)
```


```{r}
#listing religious groups
religion_columns <- c( "chrstgen", "judgen", "islmgen", "budgen", "zorogen", "hindgen", 
                      "sikhgen", "shntgen", "bahgen", "taogen", "jaingen", "confgen", 
                      "syncgen", "anmgen", "nonrelig", "othrgen")

#creating a variable with the most popular one (highest population)
religion <- religion %>%
  rowwise() %>%
  mutate(
    largest_religion = religion_columns[which.max(c_across(all_of(religion_columns)))]
  ) %>%
  ungroup()

#selecting only needed columns
religion <- religion[c('name', 'largest_religion')]
```

```{r}
as.vector(religion['name'])
```


The data is not using ISO 3166-1 alpha-3 country codes. We have to match them manually:
```{r}
mapping <- data.frame(
  custom_code = c("USA", "CAN", "BHM", "CUB", "HAI", "DOM", "JAM", "TRI", "BAR", "DMA", 
                  "GRN", "SLU", "SVG", "AAB", "SKN", "MEX", "BLZ", "GUA", "HON", "SAL", 
                  "NIC", "COS", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
                  "BOL", "PAR", "CHL", "ARG", "URU", "UKG", "IRE", "NTH", "BEL", "LUX", 
                  "FRN", "MNC", "LIE", "SWZ", "SPN", "AND", "POR", "GMY", "POL", "AUS", 
                  "HUN", "CZR", "SLO", "ITA", "SNM", "MLT", "ALB", "MNG", "MAC", "CRO", 
                  "YUG", "BOS", "KOS", "SLV", "GRC", "CYP", "BUL", "MLD", "ROM", "RUS", 
                  "EST", "LAT", "LIT", "UKR", "BLR", "ARM", "GRG", "AZE", "FIN", "SWD", 
                  "NOR", "DEN", "ICE", "CAP", "STP", "GNB", "EQG", "GAM", "MLI", "SEN", 
                  "BEN", "MAA", "NIR", "CDI", "GUI", "BFO", "LBR", "SIE", "GHA", "TOG", 
                  "CAO", "NIG", "GAB", "CEN", "CHA", "CON", "DRC", "UGA", "KEN", "TAZ", 
                  "BUI", "RWA", "SOM", "DJI", "ETH", "ERI", "ANG", "MZM", "ZAM", "ZIM", 
                  "MAW", "SAF", "NAM", "LES", "BOT", "SWA", "MAG", "COM", "MAS", "SEY", 
                  "MOR", "ALG", "TUN", "LIB", "SUD", "IRN", "TUR", "IRQ", "EGY", "SYR", 
                  "LEB", "JOR", "ISR", "SAU", "YEM", "KUW", "BAH", "QAT", "UAE", "OMA", 
                  "AFG", "TKM", "TAJ", "KYR", "UZB", "KZK", "CHN", "TAW", "PRK", "ROK", 
                  "JPN", "IND", "BHU", "PAK", "BNG", "MYA", "SRI", "MAD", "NEP", "THI", 
                  "CAM", "LAO", "DRV", "MAL", "SIN", "BRU", "PHI", "INS", "ETM", "AUL", 
                  "PNG", "NEW", "VAN", "SOL", "KIR", "TUV", "FIJ", "TON", "NAU", "MSI", 
                  "PAL", "FSM", "WSM"),
  iso3c = c("USA", "CAN", "BHS", "CUB", "HTI", "DOM", "JAM", "TTO", "BRB", "DMA", 
            "GRD", "LCA", "VCT", "ATG", "KNA", "MEX", "BLZ", "GTM", "HND", "SLV", 
            "NIC", "CRI", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
            "BOL", "PRY", "CHL", "ARG", "URY", "GBR", "IRL", "NLD", "BEL", "LUX", 
            "FRA", "MCO", "LIE", "CHE", "ESP", "AND", "PRT", "DEU", "POL", "AUT", 
            "HUN", "CZE", "SVK", "ITA", "SMR", "MLT", "ALB", "MNE", "MKD", "HRV", 
            "YUG", "BIH", "XKX", "SVN", "GRC", "CYP", "BGR", "MDA", "ROU", "RUS", 
            "EST", "LVA", "LTU", "UKR", "BLR", "ARM", "GEO", "AZE", "FIN", "SWE", 
            "NOR", "DNK", "ISL", "CPV", "STP", "GNB", "GNQ", "GMB", "MLI", "SEN", 
            "BEN", "MAR", "NER", "CIV", "GIN", "BFA", "LBR", "SLE", "GHA", "TGO", 
            "CMR", "NGA", "GAB", "CAF", "TCD", "COG", "COD", "UGA", "KEN", "TZA", 
            "BDI", "RWA", "SOM", "DJI", "ETH", "ERI", "AGO", "MOZ", "ZMB", "ZWE", 
            "MWI", "ZAF", "NAM", "LSO", "BWA", "SWZ", "MDG", "COM", "MUS", "SYC", 
            "MAR", "DZA", "TUN", "LBY", "SDN", "IRN", "TUR", "IRQ", "EGY", "SYR", 
            "LBN", "JOR", "ISR", "SAU", "YEM", "KWT", "BHR", "QAT", "ARE", "OMN", 
            "AFG", "TKM", "TJK", "KGZ", "UZB", "KAZ", "CHN", "TWN", "PRK", "KOR", 
            "JPN", "IND", "BTN", "PAK", "BGD", "MMR", "LKA", "MDV", "NPL", "THA", 
            "KHM", "LAO", "VNM", "MYS", "SGP", "BRN", "PHL", "IDN", "TLS", "AUS", 
            "PNG", "NZL", "VUT", "SLB", "KIR", "TUV", "FJI", "TON", "NRU", "WSM", 
            "PLW", "FSM", "WSM")
)

#merging religion with mapping
religion <- religion |>
  left_join(mapping, by = c("name" = "custom_code")) |>
  mutate(name = ifelse(!is.na(iso3c), iso3c, name)) |>
  select(-iso3c)
```


```{r}
#which religious groups are the most popular
unique(religion['largest_religion'])
```

```{r}
# countries where majority of population is non-religious
religion |> 
  filter(largest_religion == 'nonrelig')
```

```{r}
#sorting alphabetically
religion <- religion |> 
  arrange(name)
```


## US Aid Data

Data source: https://results.usaid.gov/results/country?fiscalYear=2023
```{r}
usaid <- readxl::read_excel("d2r_complete_data.xlsx")
```

```{r}
#choosing the latest year
usaid <- usaid %>% 
  filter(fiscal_year == 2022) #including only 2023 and 2024

head(usaid)
```

```{r}
unique(usaid['country_name'])
```

```{r}
unique(usaid['sector_name'])
```

```{r}
#summing the values
usaid <- usaid %>% 
  group_by(country_name) %>%
  summarize(total_disbursements = sum(disbursements, na.rm = TRUE))
```


```{r}
country_names <- usaid$country_name
#converting country names to iso3c country codes
usaid$country_text_id <- countrycode::countrycode(country_names, 
                                              origin = "country.name", 
                                              destination = "iso3c")

usaid <- usaid[c("country_text_id", "total_disbursements")]
head(usaid)
```

```{r}
#dropping NAs
usaid <- drop_na(usaid)
```

```{r}
#sorting alphabetically
usaid <- usaid |> 
  arrange(country_text_id)
```


## GDP Dataset

```{r}
#importing GDP dataset
gdp <- readr::read_csv('gdp_data.csv')
```
```{r}
#renaming the column
gdp$country_text_id <- gdp$`Country Code`

#dropping unnecessary columns
gdp$`Country Code` <- NULL
gdp$...1 <- NULL
```


## Covariate dataset

```{r}
# democracy index covariate
countries <- incidence_matrix_df$ms_code

node_df <- data.frame(country_text_id = countries)

#merging with religion
names(religion)[1] <- "country_text_id" #renaming the country column
node_df <- node_df |>
  left_join(religion, by = "country_text_id")

# merging with democracy scores
node_df <- node_df |>
  left_join(democracy, by = "country_text_id")

# using mean scores to fill in missing values
node_df$v2x_polyarchy[is.na(node_df$v2x_polyarchy)] <- mean(node_df$v2x_polyarchy, na.rm = TRUE)

#merging USAID data into node_df
node_df <- node_df |>
  left_join(usaid, by = "country_text_id")

#filling missing USAID values with 0
node_df$total_disbursements[is.na(node_df$total_disbursements)] <- 0

#merging with GDP
node_df <- node_df |>
  left_join(gdp, by = "country_text_id")
```


```{r}
node_df[apply(is.na(node_df), 1, any), ]
```

Missing religion for Mauritania, Mongolia, Serbia. They will be filled in manually with the data from [WorldPopulationReviw](https://worldpopulationreview.com/country-rankings/religion-by-country) that got data from CIA, UN, etc.
```{r}
#manually filling in the data
node_df <- node_df |>
  mutate(largest_religion = case_when(
    country_text_id == 'MRT' ~ 'islmgen',
    country_text_id == 'MNG' ~ 'budgen',
    country_text_id == 'SRB' ~ 'chrstgen',
    TRUE ~ largest_religion))
```


```{r}
#matching node_df rows with the rows of incidence matrix
node_df <- node_df[match(incidence_matrix_df$ms_code, node_df$country_text_id), ]
```



```{r}
vertex_name <- node_df$country_text_id
resolutions <- c('ARESES-1021', 'ARES78170', 'ARESES-1023', 
                      'ARES7876', 'ARESES-1022', 'ARES7877', 'ARES7878') #resolution names

vertex_name <- append(vertex_name, resolutions)
vertex_name
```




```{r}
#setting vertex attributes
network::set.vertex.attribute(UNGA, "vertex.names", vertex_name)
network::set.vertex.attribute(UNGA, "democracy_score", node_df$v2x_polyarchy, v = 1:176)
network::set.vertex.attribute(UNGA, "religion", node_df$largest_religion, v = 1:176)
network::set.vertex.attribute(UNGA, "USAid", node_df$total_disbursements, v = 1:176)
network::set.vertex.attribute(UNGA, "GDP", node_df$gdp, v = 1:176)
```



```{r}
network::set.vertex.attribute(UNGA, "bipartite", value = rep(176, 176), v = 1:176)
```


```{r}
# Degree partition 1 (countries)
summary(UNGA ~ b1degree(1:7))
# Degree partition 2 (resolutions)
summary(UNGA ~ b2degree(1:176))
```


# Model
Hypothesis 1. The popularity effects; some resolutions are more popular than others in a sense that more countries vote in favor of them. For instance some countries may care more about humanitarian issues rather than about territorial disputes. Some resolutions maybe more extreme than others, so if a country votes for it, it condemns Israel more **b2star**, **b2sociality(nodes=-1)**

**gwb2nsp**. 


```{r}
# Model 1. Just edges
model1 <-ergm::ergm(UNGA ~ edges,
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model1)
```


```{r}
#Model 2. Adding b2star(2)
model2 <-ergm::ergm(UNGA ~ edges + b2star(2),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model2)
```


```{r}
ergm::mcmc.diagnostics(model2)
```

```{r}
#table with models
texreg::screenreg(list(model1, model2))
```



```{r}
# Same as model 2 but trying with constraints
model22 <-ergm::ergm(UNGA ~ edges + b2star(2),
                    constraints = ~bd(minout = 0, maxout = c(rep(7, 176), rep(Inf, 7))),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model22)
```




```{r}
# Model 3. Adding b2sociality
model3 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2sociality(nodes=-1),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 15,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model3)
```


```{r}
#table with models
texreg::screenreg(list(model1, model2, model3))
```

```{r}
# MCMC diagnostics of model3
ergm::mcmc.diagnostics(model3)
```




```{r}
# Model 4. Adding democracy score
model3 <-ergm::ergm(UNGA ~ edges + b1star(2) + b1cov("democracy_score"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model4)
```







```{r}

```


Trying balanced religion:
```{r}
node_df$largest_religion <- 
  ifelse(node_df$largest_religion %in% 
           c("anmggen", "budgen", "hindgen", "judgen", "nonrelig", 
             "shntgen", "syncgen", "anmgen"),"other",
         node_df$largest_religion)

table(node_df$largest_religion)

#updating network covariate
network::set.vertex.attribute(UNGA, "largest_religion", node_df$largest_religion)
```

The `b2sociality(nodes=-1)` term examines whether some resolutions generally receive more votes than others, regardless of specific country-level patterns.
```{r}
model4 <-ergm::ergm(UNGA ~ edges + b1star(2) + b2sociality(nodes=-1) + 
                      b1cov("democracy_score"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model4)
```

```{r}
ergm::mcmc.diagnostics(model4)
```


# Trial

```{r}
mdata <- matrix(
  c(1, 1, 1, 1,
    1, 1, 0, 0,
    1, 1, 1, 0,
    1, 1, 0, 0,
    1, 1, 0, 1,
    0, 1, 1, 1,
    0, 0, 1, 1,
    1, 0, 1, 1,
    0, 0, 1, 1,
    0, 0, 1, 1), 
  nrow = 10,  # Number of rows
  ncol = 4,   # Number of columns
  byrow = TRUE # Fill matrix row by row
)

# Print the matrix
print(mdata)
```

```{r}
kidsnet <- network::network(mdata, directed = FALSE, bipartite = TRUE)
kidsnet
```

```{r}
network::set.vertex.attribute(kidsnet, "bipartite", value = rep(10, 10), v = 1:10)
kidsnet
```

```{r}
# Degree partition 1 (kids)
summary(kidsnet ~ b1degree(1:10))
# Degree partition 2 (play-dates)
summary(kidsnet ~ b2degree(1:10))
```

```{r}
Age <- c(11, 11, 10, 12, 11, 10, 13, 11, 10, 12)

network::set.vertex.attribute(kidsnet, "Age", Age, v = 1:10)
#network::set.vertex.attribute(kidsnet, "bipartite", value = rep(10, 10), v = 1:10)
network::get.vertex.attribute(kidsnet, "Age")
```


```{r}
# Degree partition 1 (kids)
summary(kidsnet ~ b1degree(1:10))
# Degree partition 2 (play-dates)
summary(kidsnet ~ b2degree(1:10))
```



