---
title: "UNGA_bipartite"
output:
  pdf_document:
    toc: true
    toc_depth: '3'
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE) # ignore the errors
set.seed(123) #set the seed for consistent results

#libraries
library(dplyr)
library(tidyverse)
```


# Datasets
## UNGA

```{r}
#UNGA dataset

assembly <- readr::read_csv("2024_09_12_ga_resolutions_voting.csv")
#assembly <- readexcel::read_excel("2024_09_12_ga_resolutions_voting.xls")
head(assembly)
```
Country name descrepancies: Yogoslavia republik, USSR, Ukranian SSR, Belorussian SSR, Turkey and Turkiye, East and West Germany, Former Yugoslav Republic of Macedonia, Serbia and Montenegro, etc.


```{r}
unique(assembly['modality'])
```

We chose years 2023 and 2024 for the Palestine Topic because of the events that happened in Gaza in October 2023.
```{r}
# working with the date variable
assembly <- assembly |> dplyr::mutate(date = lubridate::ymd(date))

data <- assembly %>% 
  dplyr::mutate(year = lubridate::year(date)) %>% #changing year variable
  filter(year %in% c(2023, 2024)) #including only 2023 and 2024
```


```{r}
#how many countries are in UN
unique(data['ms_code'])
```


```{r}
unique(data['title'])
```

```{r}
unique(data['subjects'])
```

**Related topics**: PALESTINE QUESTION, TERRITORIES OCCUPIED BY ISRAEL--SETTLEMENT POLICY, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS--REPORTS, TERRITORIES OCCUPIED BY ISRAEL--NATURAL RESOURCES, TERRITORIES OCCUPIED BY ISRAEL--HUMAN RIGHTS
```{r}
# include subject where words PALESTINE and ISRAEL are present
data <- data |> 
  filter(stringr::str_detect(subjects, "PALESTINE|ISRAEL"))
```


```{r}
#include only these variables
data <- data[c('ms_code', 'ms_vote', 'resolution', 
                                       'title')]
# deleting NV votes
data <- data |> 
  filter(ms_vote != "NV")
```
About 100 votes were NV


```{r}
#checking for duplicates
nrow(unique(data)) == nrow(data)
```
no duplicates

```{r}
#which resolutions are held
unique(data['title'])
```

Six titles overall that are about Palestine-Israel conflict.
**Seven** resolutions.
```{r}
data |>
  group_by(resolution) |>
  summarise(vote_count = n())
```

```{r}
data |> 
  filter(ms_code == 'ISR')
```
Israel voted 'No' in all seven resolutions.


```{r}
#sorting alphabetically
data <- data |> 
  arrange(ms_code)
```


```{r}
write.csv(data, file = "data.csv", row.names = FALSE)
```




### Making a Bipartite network
While unimodal networks can also be represented by adjacency matrices, bipartite networks require **incidence matrices**.

```{r}
incidence_matrix_df <- data %>%
  filter(ms_vote == 'Y') %>%                 # Filter Yes votes
  select(ms_code, resolution, ms_vote) %>%      # Select relevant columns
  mutate(value = 1) %>%                # Assign value 1 for edges
  pivot_wider(names_from = resolution, # Create columns for resolutions
              values_from = value,
              values_fill = 0)         # Fill missing values with 0

# Convert to a matrix
incidence_matrix <- as.matrix(incidence_matrix_df[,-1])  # Exclude country names
colnames(incidence_matrix) <- NULL
```




```{r}
data$vote_binary <- ifelse(data$ms_vote == "Y", 1, 0)

# Create the incidence matrix
library(tidyr)
incidence_matrix_df <- data %>%
  select(ms_code, resolution, vote_binary) %>%
  pivot_wider(names_from = resolution, values_from = vote_binary, values_fill = 0)

incidence_matrix <- as.matrix(incidence_matrix_df[,-1])  # Exclude country names
colnames(incidence_matrix) <- NULL
print(incidence_matrix)
```


```{r}
any(is.na(incidence_matrix))
```


```{r}
#matrix dimensions
dim(incidence_matrix)
```


```{r}
UNGA <- network::network(incidence_matrix, directed = FALSE, bipartite = TRUE)
UNGA
```


```{r}
network::set.vertex.attribute(UNGA, "bipartite", value = rep(190, 190), v = 1:190)
UNGA
```

```{r}
# Degree partition 1 (countries)
summary(UNGA ~ b1degree(1:7))
# Degree partition 2 (resolutions)
summary(UNGA ~ b2degree(1:190))
```



## Democracy Data

```{r}
# V-Dem project
democracy <- readr::read_csv("V-Dem-CY-Full+Others-v14.csv")
```

```{r}
#choosing the latest available year
democracy <- democracy |> 
  filter(year == 2023)

#leaving only needed columns
democracy <- democracy[c('country_text_id', 'v2x_polyarchy', 'v2x_libdem', 
                       'v2x_partipdem', 'v2x_delibdem', 'v2x_egaldem')]
```
**v2x_polyarchy** - To what extent is the ideal of electoral democracy in its fullest sense achieved?
**v2x_libdem** - To what extent is the ideal of liberal democracy achieved?
**v2x_partipdem** - To what extent is the ideal of participatory democracy achieved?
**v2x_delibdem** - To what extent is the ideal of deliberative democracy achieved?
**v2x_egaldem** - To what extent is the ideal of egalitarian democracy achieved? (rights are protected equally across all groups)

```{r}
#checking correlations
cor.test(democracy$v2x_polyarchy, democracy$v2x_partipdem, method = "pearson")
```

```{r}
cor.test(democracy$v2x_polyarchy, democracy$v2x_egaldem, method = "pearson")
```
Since they are highly correlated, we are choosing only electoral democracy score.
```{r}
democracy <- democracy[c('country_text_id', 'v2x_polyarchy')]
```

```{r}
#arranging countries alphabetically
democracy <- democracy |> 
  arrange(country_text_id)
```



## Religion Data
```{r}
#importing the dataset
religion <- readr::read_csv('WRP_national.csv')
```

```{r}
#picking the most recent year
religion <- religion |> 
  filter(year == 2010)
```


```{r}
#listing religious groups
religion_columns <- c( "chrstgen", "judgen", "islmgen", "budgen", "zorogen", "hindgen", 
                      "sikhgen", "shntgen", "bahgen", "taogen", "jaingen", "confgen", 
                      "syncgen", "anmgen", "nonrelig", "othrgen")

#creating a variable with the most popular one (highest population)
religion <- religion %>%
  rowwise() %>%
  mutate(
    largest_religion = religion_columns[which.max(c_across(all_of(religion_columns)))]
  ) %>%
  ungroup()

#selecting only needed columns
religion <- religion[c('name', 'largest_religion')]
```

```{r}
as.vector(religion['name'])
```


The data is not using ISO 3166-1 alpha-3 country codes. We have to match them manually:
```{r}
mapping <- data.frame(
  custom_code = c("USA", "CAN", "BHM", "CUB", "HAI", "DOM", "JAM", "TRI", "BAR", "DMA", 
                  "GRN", "SLU", "SVG", "AAB", "SKN", "MEX", "BLZ", "GUA", "HON", "SAL", 
                  "NIC", "COS", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
                  "BOL", "PAR", "CHL", "ARG", "URU", "UKG", "IRE", "NTH", "BEL", "LUX", 
                  "FRN", "MNC", "LIE", "SWZ", "SPN", "AND", "POR", "GMY", "POL", "AUS", 
                  "HUN", "CZR", "SLO", "ITA", "SNM", "MLT", "ALB", "MNG", "MAC", "CRO", 
                  "YUG", "BOS", "KOS", "SLV", "GRC", "CYP", "BUL", "MLD", "ROM", "RUS", 
                  "EST", "LAT", "LIT", "UKR", "BLR", "ARM", "GRG", "AZE", "FIN", "SWD", 
                  "NOR", "DEN", "ICE", "CAP", "STP", "GNB", "EQG", "GAM", "MLI", "SEN", 
                  "BEN", "MAA", "NIR", "CDI", "GUI", "BFO", "LBR", "SIE", "GHA", "TOG", 
                  "CAO", "NIG", "GAB", "CEN", "CHA", "CON", "DRC", "UGA", "KEN", "TAZ", 
                  "BUI", "RWA", "SOM", "DJI", "ETH", "ERI", "ANG", "MZM", "ZAM", "ZIM", 
                  "MAW", "SAF", "NAM", "LES", "BOT", "SWA", "MAG", "COM", "MAS", "SEY", 
                  "MOR", "ALG", "TUN", "LIB", "SUD", "IRN", "TUR", "IRQ", "EGY", "SYR", 
                  "LEB", "JOR", "ISR", "SAU", "YEM", "KUW", "BAH", "QAT", "UAE", "OMA", 
                  "AFG", "TKM", "TAJ", "KYR", "UZB", "KZK", "CHN", "TAW", "PRK", "ROK", 
                  "JPN", "IND", "BHU", "PAK", "BNG", "MYA", "SRI", "MAD", "NEP", "THI", 
                  "CAM", "LAO", "DRV", "MAL", "SIN", "BRU", "PHI", "INS", "ETM", "AUL", 
                  "PNG", "NEW", "VAN", "SOL", "KIR", "TUV", "FIJ", "TON", "NAU", "MSI", 
                  "PAL", "FSM", "WSM"),
  iso3c = c("USA", "CAN", "BHS", "CUB", "HTI", "DOM", "JAM", "TTO", "BRB", "DMA", 
            "GRD", "LCA", "VCT", "ATG", "KNA", "MEX", "BLZ", "GTM", "HND", "SLV", 
            "NIC", "CRI", "PAN", "COL", "VEN", "GUY", "SUR", "ECU", "PER", "BRA", 
            "BOL", "PRY", "CHL", "ARG", "URY", "GBR", "IRL", "NLD", "BEL", "LUX", 
            "FRA", "MCO", "LIE", "CHE", "ESP", "AND", "PRT", "DEU", "POL", "AUT", 
            "HUN", "CZE", "SVK", "ITA", "SMR", "MLT", "ALB", "MNE", "MKD", "HRV", 
            "YUG", "BIH", "XKX", "SVN", "GRC", "CYP", "BGR", "MDA", "ROU", "RUS", 
            "EST", "LVA", "LTU", "UKR", "BLR", "ARM", "GEO", "AZE", "FIN", "SWE", 
            "NOR", "DNK", "ISL", "CPV", "STP", "GNB", "GNQ", "GMB", "MLI", "SEN", 
            "BEN", "MAR", "NER", "CIV", "GIN", "BFA", "LBR", "SLE", "GHA", "TGO", 
            "CMR", "NGA", "GAB", "CAF", "TCD", "COG", "COD", "UGA", "KEN", "TZA", 
            "BDI", "RWA", "SOM", "DJI", "ETH", "ERI", "AGO", "MOZ", "ZMB", "ZWE", 
            "MWI", "ZAF", "NAM", "LSO", "BWA", "SWZ", "MDG", "COM", "MUS", "SYC", 
            "MAR", "DZA", "TUN", "LBY", "SDN", "IRN", "TUR", "IRQ", "EGY", "SYR", 
            "LBN", "JOR", "ISR", "SAU", "YEM", "KWT", "BHR", "QAT", "ARE", "OMN", 
            "AFG", "TKM", "TJK", "KGZ", "UZB", "KAZ", "CHN", "TWN", "PRK", "KOR", 
            "JPN", "IND", "BTN", "PAK", "BGD", "MMR", "LKA", "MDV", "NPL", "THA", 
            "KHM", "LAO", "VNM", "MYS", "SGP", "BRN", "PHL", "IDN", "TLS", "AUS", 
            "PNG", "NZL", "VUT", "SLB", "KIR", "TUV", "FJI", "TON", "NRU", "WSM", 
            "PLW", "FSM", "WSM")
)

#merging religion with mapping
religion <- religion |>
  left_join(mapping, by = c("name" = "custom_code")) |>
  mutate(name = ifelse(!is.na(iso3c), iso3c, name)) |>
  select(-iso3c)
```


```{r}
#which religious groups are the most popular
unique(religion['largest_religion'])
```

```{r}
# countries where majority of population is non-religious
religion |> 
  filter(largest_religion == 'nonrelig')
```

```{r}
#sorting alphabetically
religion <- religion |> 
  arrange(name)
```


## US Aid Data

Data source: https://results.usaid.gov/results/country?fiscalYear=2023
```{r}
usaid <- readxl::read_excel("d2r_complete_data.xlsx")
```

```{r}
#choosing the latest year
usaid <- usaid %>% 
  filter(fiscal_year == 2022) #including only 2023 and 2024

head(usaid)
```

```{r}
unique(usaid['country_name'])
```

```{r}
unique(usaid['sector_name'])
```

```{r}
#summing the values
usaid <- usaid %>% 
  group_by(country_name) %>%
  summarize(total_disbursements = sum(disbursements, na.rm = TRUE))
```


```{r}
country_names <- usaid$country_name
#converting country names to iso3c country codes
usaid$country_text_id <- countrycode::countrycode(country_names, 
                                              origin = "country.name", 
                                              destination = "iso3c")

usaid <- usaid[c("country_text_id", "total_disbursements")]
head(usaid)
```

```{r}
#dropping NAs
usaid <- drop_na(usaid)
```

```{r}
#sorting alphabetically
usaid <- usaid |> 
  arrange(country_text_id)
```


## GDP Dataset

```{r}
#importing GDP dataset
gdp <- readr::read_csv('gdp_data.csv')
```

```{r}
#renaming the column
gdp$country_text_id <- gdp$`Country Code`

#dropping unnecessary columns
gdp$`Country Code` <- NULL
gdp$...1 <- NULL
```


## Covariate dataset

```{r}
# democracy index covariate
countries <- incidence_matrix_df$ms_code

node_df <- data.frame(country_text_id = countries)

#merging with religion
names(religion)[1] <- "country_text_id" #renaming the country column
node_df <- node_df |>
  left_join(religion, by = "country_text_id")

# merging with democracy scores
node_df <- node_df |>
  left_join(democracy, by = "country_text_id")

# using mean scores to fill in missing values
node_df$v2x_polyarchy[is.na(node_df$v2x_polyarchy)] <- mean(node_df$v2x_polyarchy, na.rm = TRUE)

#merging USAID data into node_df
node_df <- node_df |>
  left_join(usaid, by = "country_text_id")

#filling missing USAID values with 0
node_df$total_disbursements[is.na(node_df$total_disbursements)] <- 0

#merging with GDP
node_df <- node_df |>
  left_join(gdp, by = "country_text_id")
```


```{r}
node_df[apply(is.na(node_df), 1, any), ]
```

Missing religion for Marshall Islands, Mauritania, Mongolia, Serbia, and South Sudan. They will be filled in manually with the data from [WorldPopulationReviw](https://worldpopulationreview.com/country-rankings/religion-by-country) that got data from CIA, UN, etc.
```{r}
#manually filling in the data
node_df <- node_df |>
  mutate(largest_religion = case_when(
    country_text_id == 'MHL' ~ 'chrstgen',
    country_text_id == 'MRT' ~ 'islmgen',
    country_text_id == 'MNG' ~ 'budgen',
    country_text_id == 'SRB' ~ 'chrstgen',
    country_text_id == 'SSD' ~ 'chrstgen',
    TRUE ~ largest_religion))
```


```{r}
#matching node_df rows with the rows of incidence matrix
node_df <- node_df[match(incidence_matrix_df$ms_code, node_df$country_text_id), ]
```

We have decided to make religion variable binomial:
```{r}
#dummifying religion column. If country is islamic, the value = 1. If other - 0.
node_df$if_islamic <- ifelse(node_df$largest_religion == "islmgen", 1, 0)
node_df$largest_religion <- NULL
```


## Covariates EDA

```{r}
# inspecting the dataframe
head(node_df)
summary(node_df)
```
The dataset contains information about 190 countries, including their democracy index score, total government disbursements, GDP, and whether the country is Islamic or not. The democracy index scores range from 0.015 to 0.915, with the majority of countries falling in the middle range. Government disbursements and GDP vary significantly, with many countries having low values. Most of the countries in the dataset are non-Islamic.

```{r}
# making histogram to check distribution of the democracy index score
hist(node_df$v2x_polyarchy, main = "Distribution of Democracy Index Score", col = "lightblue", breaks = 20,
xlab = "Democracy Index Score", prob = TRUE)
lines(density(node_df$v2x_polyarchy))
```

We can see that there is a significant proportion of countries in the dataset have a democracy index score between 0.5-0.6, which means that the majority of countries have characteristics of both democratic and authoritarian regimes. With regards to more extreme regimes, either democratic or authoritarian, these seem to be more evenly distributed. 


```{r}
high_disbursement_country <- node_df[node_df$total_disbursements > 2500000000, "country_text_id"]
print(high_disbursement_country)

filtered_df <- node_df[node_df$total_disbursements <= 2500000000, ]

ggplot(node_df, aes(x = factor(if_islamic), y = total_disbursements)) +
  geom_boxplot(fill = "lightblue", outlier.color = "red", outlier.shape = 16) +
  labs(
    x = "Islamic",
    y = "Total Disbursements",
    title = "Total Disbursements by Islamic Indicator"
  )
```

One country (UKR) was found to receive significantly more disimbursements compared to other countries, which made the visualization uninterpretable. Therefore, this country was temporarily removed from the dataset to be able to see the general relationship of Islamic countries and their total disbursements. The boxplots show that Islamic countries seem to have a higher average total disimbursements compared to non-Islamic countries. 

```{r}
filtered_df <- node_df[node_df$total_disbursements <= 2500000000, ]

# make scatterplot of relationship between GDP and total disbursement
ggplot(filtered_df, aes(x = gdp, y = total_disbursements)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "red", se = TRUE) +
  labs(
    x = "GDP",
    y = "Total Disbursements",
    title = "GDP vs Total Disbursements"
  )
```
The scatterplot shows a negative relationship between a country's GDP and the total disbursements it receives. This means that as the GDP of a country increases, the total disbursements it receives tend to decrease, which makes sense as richer countries are generally less dependent on foreign aid. However, the relationship is not very strong, as indicated by the scattered points and the wide confidence interval. This suggests that other factors besides GDP may also influence the amount of disbursements a country receives.


```{r}
vertex_name <- node_df$country_text_id
resolutions <- c('ARESES-1021', 'ARES78170', 'ARESES-1023', 
                      'ARES7876', 'ARESES-1022', 'ARES7877', 'ARES7878') #resolution names

vertex_name <- append(vertex_name, resolutions)
vertex_name
```


```{r}
#setting vertex attributes
network::set.vertex.attribute(UNGA, "vertex.names", vertex_name)
network::set.vertex.attribute(UNGA, "democracy_score", node_df$v2x_polyarchy, v = 1:190)
network::set.vertex.attribute(UNGA, "islamic", node_df$if_islamic, v = 1:190)
network::set.vertex.attribute(UNGA, "USAid", node_df$total_disbursements, v = 1:190)
network::set.vertex.attribute(UNGA, "GDP", node_df$gdp, v = 1:190)
```



```{r}
network::set.vertex.attribute(UNGA, "bipartite", c(rep(0, 190), rep(1, 7)))
```


```{r}
# Degree partition 1 (countries)
summary(UNGA ~ b1degree(1:7))
# Degree partition 2 (resolutions)
summary(UNGA ~ b2degree(1:190))
```


```{r}
bipartite_attr <- network::get.vertex.attribute(UNGA, "bipartite")
print(bipartite_attr)  # This should show 0 for countries and 1 for resolutions.
```



```{r}
# Identify indices of resolutions
resolution_indices <- which(bipartite_attr == 1)

# Extract degrees for resolutions
resolution_degrees <- sna::degree(UNGA, cmode = "indegree")[resolution_indices]

# Get resolution names
resolution_names <- network::get.vertex.attribute(UNGA, "vertex.names")[resolution_indices]

# Create a dataframe with resolution-specific edge counts
resolution_summary <- data.frame(
  Resolution = resolution_names,
  Edges = resolution_degrees
)

# Print the summary
print(resolution_summary)
```
With the exception of resolution ARES78170 and ARESES-1021, the resolutions tend to have a similar number of votes in favor. Most countries voted in favor of all resolutions with the exception of ARES78170 as it only received 86 votes in favor out of 190 possible ones. The resolution with the highest amount of votes is ARES7877

```{r}
# Identify indices of countries
resolution_indices <- which(bipartite_attr == 0)

# Extract degrees for countries
resolution_degrees <- sna::degree(UNGA, cmode = "indegree")[resolution_indices]

# Get country names
resolution_names <- network::get.vertex.attribute(UNGA, "vertex.names")[resolution_indices]

# Create a dataframe with country-specific edge counts
resolution_summary <- data.frame(
  Country = resolution_names,
  Edges = resolution_degrees
)

# Print the summary
print(resolution_summary)
```
```{r}
#library(ggplot2)
# density graph showing the distribution of times countries voted towards resolutions
ggplot2::ggplot(resolution_summary, aes(x=Edges)) +
    ggplot2::geom_density() + ggplot2::ggtitle("Distribution of Votes in Favor of Resolutions") +
  theme_classic()
```

The notable peak around 6-7 edges, indicate that many countries tend to vote in favor of most or all resolutions (6-7 out of 7 possible resolutions). There's relatively low density between 0-2 edges, showing that very few countries did not vote in favor or did so for only a few resolutions. There's a gradual increase in density starting around 4 edges, with the steepest increase occurring between 5-6 edges. This indicates that the most common pattern is for countries to vote in favor of a majority of resolutions.

```{r}
#Network's density
snafun::g_density(UNGA)
```
The high density reveals that our network is quite dense as 72% of all possible edge connections in this network exist. This is in accordance to our density graph above as it illustrates a tendency for countries to vote for 6 or 7 resolutions resulting in a highly connected network. 

Since we are dealing with a bipartite network, to be able to measure other things such as transitivity, subgroups, etc.  we will project the network and make it unipartite. Note: this is only done for this purpose, for the rest of the analysis we will continue using our bipartite network 

```{r}
# making the network unipartite
UNGA_i <- snafun::to_igraph(UNGA)
projected_UNGA <- igraph::bipartite_projection(UNGA_i)
projected_UNGA


```
As we can see from the number of nodes and edges, the first projection is our countries one. We will not focus on the second partition as this network is fully connected considering that there are countries that voted for all resolutions.
```{r}
# saving countries projection 
country_network_i <- projected_UNGA$proj1
country_network_i
```

We proceed with our network measures.
```{r}
snafun::g_summary(country_network_i)
```
This network, as our original, has 190 countries however the number of edges has tremendously increased from 960 to 15103 because in this format a single vote in favor connects one country to at least 85 other ones (minimum number of votes in favor of resolution ARES78170 minus one) 

The transitivity score of our network is extremely large, indicating that if country A and B vote similarly (both in favor) on a resolutions, and B and C vote in favor of some resolution, then it's almost certain (98.4% of the time) that A and C also vote similarly. The high transitivity indicates high consistency in voting patterns in resolutions, *and a high tendency of voting in cohesive groups*. **not sure about this part**

Looking at the density of the network we can see that after projection it increased from 72.1% to 84.1%. This makes sense as when projecting a lot of countries get connected even when they share one vote. The increase to 84.1% in the projected country-country network means that 84.1% of all possible pairs of countries share at least one common "yes" vote. 

The dyad census reveals that there are 15103 mutual edges in this network (equivalent to number of edges in this network since undirected) while the null value of 2852 represents the number of edges that could have been formed. This once again reveals that our network is highly connected as mutual edges are much larger than null. 

Reciprocity score has no meaning since network is undirected. 

There are 14 isolates in our network. 14 countries did not vote in favor for any of the resolutions. The following code displays the country codes of the isolates.
```{r}
snafun::extract_isolates(country_network_i)
```
Cameroon, Federate Sates of Micronesia, Israel, Kiribati, Liberia, Marshall Islands, Nauru, Palau, Papua New Guinea, Paraguay, Togo, Tonga, and the United States did not vote in favor of any resolutions. 

```{r}
snafun::plot_centralities(country_network_i)
```
There is relatively more variability in betweenness centrality score in comparison to the others. Betweenness centrality measures the amount of stress each node has relatively to the number of geodesic in the network. A lot of countries have the highest score of around 2.2, while the lowest is 0. A score of 0 means that certain countries never lie on the shortest path or act as bridges between others.        

Closeness score measures the average shorted distance between all vertices. The very narrow range (between ~0.0044 and 0.0057) indicates that closeness scores tend to be similar between all points. Only one particular country stands out as having a lower score but considering the scale the difference is not that distinctive. 

Eccentricity measures the maximum number of nodes that country have to go through to reach every other country. Most countries have an eccentricity score of 1 or 2 meaning that for any of these countries all other countries (that are connected) can be reached between 1 or 2 steps. The low values are not surprising considering how interconnected our network is. Once again the isolates of this graph can be spotted by the fact that their eccentricity scores are 0. 

The degree distribution is what we expected based on our high density score. Most countries tend to have really large degrees (150-175). The 14 isolates can be spotted on the left side of this graph. 

**CUG test**

Testing whether some of the measures are statistically signicant
```{r}
# changing it into network object so it works
country_network <- snafun::to_network(country_network_i)

# transitivity
trans_fun <- function(x, directed = FALSE) {  
  x <- snafun::fix_cug_input(x, directed = directed)
  snafun::g_transitivity(x)
}

(cug_tran <- sna::cug.test(country_network, mode = "graph", 
                                 FUN = trans_fun, 
                                 cmode = "edges", reps = 1000)) # set to edges to take into account size and density 

sna::plot.cug.test(cug_tran)
```

The p-value is statistically significant, hence, we can conclude that our transitivity is greater than most networks of this size. The black histogram (apparent as a line in this case due to scale) represents the overall distribution of the transitivity scores of the simulated networks, while the red line the score of our countries network (distinctively higher). 
```{r}
betw_fun <- function(x, directed = FALSE) {  # note: directed = FALSE!
  x <- snafun::fix_cug_input(x, directed = directed)
  snafun::g_centralize(x, measure = "betweenness", directed = directed)$centralization
}

(cug_betw <- sna::cug.test(country_network, mode = "graph", FUN = betw_fun, 
                                 cmode = "edges", 
                                 reps = 1000))
sna::plot.cug.test(cug_betw)
```

Our betweeness scores are exceptionally small for the size of our network as most tend to have a betweenness score around 0.00015. 
```{r}
closeness_fun <- function(x, directed = FALSE) {  # note: directed = FALSE!
  x <- snafun::fix_cug_input(x, directed = directed)
  snafun::g_centralize(x, measure = "closeness", directed = directed)$centralization
}

(cug_closeness <- sna::cug.test(country_network, mode = "graph", FUN = betw_fun, 
                                 cmode = "edges", 
                                 reps = 1000))
sna::plot.cug.test(cug_closeness)
```
Our closeness scores are very small in comparison to similar size networks. Our closeness score stands more to the left 

**Detecting communities**

Checking for communities, first we need to remove isolates as these algorithms tend to assign them to their own communities. The girvan and the walktrap algorithm were also considered howver they both assigned all countries into a single cluster.
```{r}
# setting seed just in case
set.seed(123)
# removing isolates
country_no_isolates <- snafun::remove_isolates(country_network_i) # need to do it with igraph object

# running louvain community detction algorithm
louvain <- snafun::extract_comm_louvain(country_no_isolates)

# check the modularity
igraph::modularity(louvain) 

# checking which community each node belongs to
igraph::membership(louvain)

snafun::plot(louvain, country_no_isolates)
```
Two communities were detected, however at first sight it appears that there is not a clear distinction of separation in terms of geography since countries from all continents appear in all clusters. Some patterns that were spotted, is that major world economies and powers such as Germany, China, France, India, Great Britain, South Korea, and Japan all appear in cluster 2 along with other quite distinctive nations. The majority of communities that have a majority muslim population and are part in the Middle East appear to be in cluster 1 although several can be found in cluster 2 (Cluster 1: Bahrain, Oman, Iran, Kuwait, Qatar, Saudi Arabia, Syria, and Turkey; Cluster 2: United Arab Emirates, Lebanon, Jordan, Yemen). The fact that no super distinctive patterns appear may be partly explained to the extremely low modularity score of 0.6% as it indicates that the divisions between communities was not strong. This highlights that UN voting patterns and international policy in general is extremely complex and cannot be explained by a few factors. Additionally, it is important to note that since we projected our network we may have lost some information in the process as this network does not make a distinction between high levels of support towards resolutions that are in favor of Palestine and low levels.    


```{r}
#table with models
texreg::screenreg(list(model1, model2))
```


```{r}
# Same as model 2 but trying with constraints
#model22 <-ergm::ergm(UNGA ~ edges + b2star(2),
#                    constraints = ~bd(minout = 0, maxout = c(rep(7, 176), rep(Inf, 7))),
#                    control = ergm::control.ergm(MCMC.burnin = 5000,
#                                                 MCMC.samplesize = 50000,
#                                                 seed = 123,
#                                                 MCMLE.maxit = 50,
 #                                                parallel = 3,
 #                                                parallel.type = "PSOCK"))
#summary(model22)
```
```{r}
#ergm::mcmc.diagnostics(model22)
```


```{r}
summary(UNGA ~ edges + b2star(2) + gwb1dsp)
```



gwb1dsp
```{r}
# Model 3. Adding gwb1dsp
model3 <-ergm::ergm(UNGA ~ edges + b2star(2) + b1degree(0),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 15,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model3)
```


```{r}
ergm::mcmc.diagnostics(model3)
```





```{r}
#table with models
texreg::screenreg(list(model1, model2, model3))
```

```{r}
# MCMC diagnostics of model3
ergm::mcmc.diagnostics(model3)
```


```{r}
# Model 4. Adding democracy score
model4 <-ergm::ergm(UNGA ~ edges + b2star(2) + 
                      b1nodematch("democracy_score", diff=TRUE),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model4)
```


```{r}
ergm::mcmc.diagnostics(model4)
```


```{r}
# Model 5. Adding religion
model5 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model5)
```


Trying balanced religion:
Muslim country - 1
```{r}
node_df$religion_balanced <- 
  ifelse(node_df$largest_religion %in% 
           c("anmggen", "budgen", "hindgen", "judgen", "nonrelig", 
             "shntgen", "syncgen", "anmgen"),"other",
         node_df$largest_religion)

table(node_df$religion_balanced)

#updating network covariate
network::set.vertex.attribute(UNGA, "religion_b", node_df$religion_balanced)
```


```{r}
#Same as model 5 but with more balanced religion
model52 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion_b"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model52)
```


```{r}
texreg::screenreg(list(model1, model2, model3, model4, model5))
```


If religion_b is still not significant, continue with `religion`.

```{r}
#Adding US Aid
model6 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion") + 
                      b1cov("USAid"),
                    control = ergm::control.ergm(MCMC.burnin = 10000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 15,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model6)
```


```{r}
#Adding GDP
model7 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2star(3) + 
                      b1cov("democracy_score") + b1nodematch("religion") + 
                      b1cov("USAid") + b1cov("GDP"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 12,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model7)
```


```{r}
#table with models
texreg::screenreg(list(model1, model2, model3, model4, model5, model6, model7))
```

```{r}
ergm::mcmc.diagnostics(model7)
```



```{r}
#Adding gwb1nsp term
model8 <-ergm::ergm(UNGA ~ edges + b2star(2) + b2sociality(nodes=-1) + 
                      gwb1nsp(0, TRUE) + 
                      b1cov("democracy_score") + b1nodematch("religion") + 
                      b1cov("USAid") + b1cov("GDP"),
                    control = ergm::control.ergm(MCMC.burnin = 5000,
                                                 MCMC.samplesize = 50000,
                                                 seed = 123,
                                                 MCMLE.maxit = 50,
                                                 parallel = 3,
                                                 parallel.type = "PSOCK"))
summary(model8)
```




# Trial

```{r}
mdata <- matrix(
  c(1, 1, 1, 1,
    1, 1, 0, 0,
    1, 1, 1, 0,
    1, 1, 0, 0,
    1, 1, 0, 1,
    0, 1, 1, 1,
    0, 0, 1, 1,
    1, 0, 1, 1,
    0, 0, 1, 1,
    0, 0, 1, 1), 
  nrow = 10,  # Number of rows
  ncol = 4,   # Number of columns
  byrow = TRUE # Fill matrix row by row
)

# Print the matrix
print(mdata)
```


```{r}
kidsnet <- network::network(mdata, directed = FALSE, bipartite = TRUE)
kidsnet
```

```{r}
network::set.vertex.attribute(kidsnet, "bipartite", value = rep(10, 10), v = 1:10)
kidsnet
```

```{r}
# Degree partition 1 (kids)
summary(kidsnet ~ b1degree(1:10))
# Degree partition 2 (play-dates)
summary(kidsnet ~ b2degree(1:10))
```

```{r}
Age <- c(11, 11, 10, 12, 11, 10, 13, 11, 10, 12)

network::set.vertex.attribute(kidsnet, "Age", Age, v = 1:10)
#network::set.vertex.attribute(kidsnet, "bipartite", value = rep(10, 10), v = 1:10)
network::get.vertex.attribute(kidsnet, "Age")
```


```{r}
# Degree partition 1 (kids)
summary(kidsnet ~ b1degree(1:10))
# Degree partition 2 (play-dates)
summary(kidsnet ~ b2degree(1:10))
```



